---
title: "Forestry Impacts on BC Pacific Salmon"
subtitle: "Musgamagw Dzawada’enuxw territory watersheds"
author: 'Maria Kuruvilla'
date: "March 2026"
output:
  pdf_document:
    toc: true
  html_document:
    collapsed: false
    fig_caption: true
    highlight: espresso
    number_sections: true
    smooth_scroll: true
    theme: sandstone
    toc: true
    toc_float: true
  word_document:
    toc: false
---


<!-- # Make a document with figures from just the MD territory watersheds -->

<!-- Have time series of spawners and time series of recruits, time series of ECA and CPD -->

<!-- # The posterior distribution of effect of forestry, effect of NPGO, effect of SST. -->

<!-- # the  productivity change with NPGO, SST, and forestry -->

<!-- # The SR Fits -->

```{=html}
<style type="text/css">

body{ /* Normal  */
      font-size: 13px;
  }
td {  /* Table  */
  font-size: 13px;
}
h1.title {
  font-size: 24px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 19px;
  color: Black;
}
h2 { /* Header 2 */
    font-size: 15px;
  color: Black;
}
h3 { /* Header 3 */
    font-size: 15px;
  color: Black;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache=FALSE)
options(max.print=23)
library(here);library(dplyr); library(stringr)
library(ggplot2)
library(tidyverse)
library(bayesplot)
library(patchwork)
library(bcmaps)
library(hues)
library(GGally)
library(latex2exp)
library(extrafont)
library(ggspatial)
```


\newpage


# Introduction

Logging has impacted many rivers in BC that support salmon. Using historical data (1950-2012) of pink salmon abundance in 417 rivers, chum salmon abundance in 374 rivers in BC, and of logging disturbance in these rivers, we estimated the impact that logging has on salmon recruitment (number of salmon produced in the next generation) using a statistical model. The two metrics of logging disturbance that we used are:

 1) Cumulative Disturbed Area (CDA) - the percent of area around a river that has been disturbed by human activities or natural disturbances without assuming any recovery within the time period of our dataset (62 years).
 2) Equivalent Clearcut Area (ECA) - proportion of area that has been clearcut around a river after accounting for an expected hydrologic recovery. This metric assumes that the forest is close to 100% recovered roughly 50 years post-logging. 
 
In addition to logging disturbance, we also used two variables to account for ocean conditions:

3) Sea-Surface Temperature (SST) - the average sea-surface temperature corresponding to the time when the salmon first enters the ocean, which is known to have variable effects on salmon recruitment.
4) North Pacific Gyre Oscillation (NPGO) - index of primary productivity in the ocean, which is known to have a positive effect on salmon recruitment. 
 
 
In this document, we have used the 4 coastwide models (with CDA for chum, with ECA for chum, with CDA for pink, and with ECA for pink) to estimate the impact of logging on some of the rivers within MD territory for which we had data. For each of these rivers, we have plotted the data of logging disturbance as given by the two metrics, ECA and CDA, and the number of salmon recruits with time. We then plotted the results of the model for that river A) the probability distributions of the effect of CDA, NPGO, and SST on salmon recruitment for that river (probability distributions with the peak to the left of 0 indicate a negative effect on salmon recruitment), B) the predicted spawner-recruit relationship for two different levels of logging disturbance experienced by the river, C) the predicted change in recruitment for different theoretical levels of logging disturbance using CDA, and D) using ECA. For figure C, the dashed line corresponds to the most recent (and highest) value of CDA experienced by the river. For figure D, the dashed line corresponds to the highest value of ECA experienced by the river. 
 



# Map of MD territory watersheds



```{r include=FALSE}
# Load the sf package
library(sf)
# Path to the GDB file
gdb_path <- here("origional-ecofish-data-models","Data","Spatial","mdfg_results.gdb")


# List all layers in the GDB
layers <- st_layers(gdb_path)

# print(layers)
# Forestry history (not a spatial dataset)
coast_forestry_timeseries <- st_read(gdb_path, layer = "CPD_ECA_salmon_watersheds_coastwide")

# Coastal salmon watersheds (spatial dataset)
coast_watersheds <- st_read(gdb_path, layer = "salmon_watersheds_coastwide")

mdfg_watersheds <- st_read(gdb_path, layer = "salmon_watersheds_MDFG")

mdfg_forestry_timeseries <- st_read(gdb_path, layer = "CPD_ECA_salmon_watersheds_MDFG")

# IF needed, you can join the datasets use the outlet feature id ("outlet_lfid" vector) and watershed group code ("wgc" vector)
# unique(coast_forestry_timeseries$outlet_lfid)
# 
# unique(coast_watersheds$outlet_lfid)
# unique(coast_watersheds$wgc)
# unique(mdfg_watersheds$wgc)

coast_forestry_timeseries_geom <- left_join(x = coast_forestry_timeseries, 
                                            coast_watersheds %>% 
                                              select(outlet_lfid,geom,wgc,NUSEDS_watershed) %>% distinct(), 
                                            by = c("outlet_lfid", "wgc"))

# glimpse(coast_watersheds %>% select(geom,wgc,NUSEDS_watershed) %>% distinct())
# glimpse(coast_forestry_timeseries)
# glimpse(coast_forestry_timeseries_geom)

#check which row has KINGCOME RIVER as NUSEDS_watershed


mdfg_forestry_timeseries_geom <- left_join(x = mdfg_forestry_timeseries, 
                                            mdfg_watersheds %>% 
                                              select(outlet_lfid,geom,wgc,NUSEDS_watershed) %>% distinct(), 
                                            by = c("outlet_lfid", "wgc"))
# 
# glimpse(mdfg_forestry_timeseries_geom)


```

```{r include=FALSE}

# Required packages ----
list.of.packages <- c("tidyverse", "extrafont", "giscoR", "ggplot2", "sf", "rmapshaper", "rnaturalearth", "patchwork", "here",
                      "bcmaps","ggsflabel") 

# What packages need to be installed?
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])] 

## Install missing packages
if (length(new.packages)) {
  install.packages(new.packages, dependencies = TRUE, repos = c("http://cran.rstudio.com/", "http://R-Forge.R-project.org"))
}

## Loading libraries
invisible(lapply(list.of.packages, library, character.only = TRUE))

# Load population sheds ----
world <- ne_countries(scale='medium',returnclass = 'sf')
Canada <- subset(world, admin == "Canada")
USA <- subset(world, admin == "United States of America")


# rivers <- lookup %>% select(River_n) %>%  filter(!is.na(River_n)) %>% pull(River_n) %>% unique()
# pop_sheds <- st_read(dsn = "data/processed/Max_ECA_sheds_Nov_2024.gpkg")  # Note that there are 1746 polygons, but only 1745 have VRI information in 2022.


#take pop sheds from mdfg_forestry_timeseries_geom

pop_sheds2 <- mdfg_forestry_timeseries_geom %>% 
  select(outlet_lfid, CPD_fmlb , NUSEDS_watershed, geom,year) %>% 
  group_by(NUSEDS_watershed) %>% 
  filter(year == max(year)) %>% 
  rename(River = NUSEDS_watershed, CPD = CPD_fmlb) %>% 
  filter(!is.na(CPD)) %>% 
  st_as_sf()

b <- st_bbox(pop_sheds2) 
bbox <- st_as_sfc(b)


#transform X_LONG and Y_LAT to 

# Watershed by region plot for forest  appendix ----
# Custom extent

bc_boundary <- bc_bound() %>% st_transform(4326)

# Globe Inset
wld <- gisco_get_countries(resolution = "20")
ortho_crs <-'+proj=ortho +lat_0=55 +lon_0=-126 +x_0=0 +y_0=0 +R=6371000 +units=m +no_defs +type=crs'

ocean <- st_point(x = c(0,0)) %>%
  st_buffer(dist = 6371000) %>% # radio Tierra
  st_sfc(crs = ortho_crs)

world <-   st_intersection(wld, st_transform(ocean, 4326)) %>%
  st_transform(crs = ortho_crs)

world_line <- ms_innerlines(world)

wld_map <- ggplot(world) +
  geom_sf(data = ocean, fill = "#deebf7", linewidth = .2) +
  geom_sf(fill = "grey50", 
          colour = NA,
          show.legend = F) +
  geom_sf(data = world_line, linewidth = .05, colour = "white") +
  geom_sf(data = bbox, col = "red", fill = NA, linewidth = 0.2) +
  scale_fill_manual(values = c("grey50", "red")) + 
  theme_void()

# wld_map
canada <- ggplot(Canada) +
  # geom_sf(data = ocean, fill = "#deebf7", linewidth = .2) +
  geom_sf(fill = "grey50", 
          colour = NA,
          show.legend = F) +
  # geom_sf(data = world_line, linewidth = .05, colour = "white") +
  geom_sf(data = bbox, col = "darkred", fill = NA, linewidth = 1) +
  scale_fill_manual(values = c("grey50", "red")) + 
  theme_void()
# canada

md_territory <- sf::st_read(here("origional-ecofish-data-models","Data", 
                                 "Spatial",
                                 "MTTT_Update.shp"), quiet = TRUE)
b <- st_bbox(pop_sheds2) 
bbox <- st_as_sfc(b)


```







```{r}

# Data wrangling

ch20rsc <- read.csv(here("origional-ecofish-data-models","Data","Processed",
                         "chum_SR_20_hat_yr_w_ocean_covariates.csv"))


#two rivers with duplicated names:
ch20rsc$River=ifelse(ch20rsc$WATERSHED_CDE=='950-169400-00000-00000-0000-0000-000-000-000-000-000-000','SALMON RIVER 2',ch20rsc$River)
ch20rsc$River=ifelse(ch20rsc$WATERSHED_CDE=="915-486500-05300-00000-0000-0000-000-000-000-000-000-000",'LAGOON CREEK 2',ch20rsc$River)


ch20rsc=ch20rsc[order(factor(ch20rsc$River),ch20rsc$BroodYear),]

ch20rsc$River_n <- as.numeric(factor(ch20rsc$River))

#normalize ECA 2 - square root transformation (ie. sqrt(x))
ch20rsc$sqrt.ECA=sqrt(ch20rsc$ECA_age_proxy_forested_only)
ch20rsc$sqrt.ECA.std=(ch20rsc$sqrt.ECA-mean(ch20rsc$sqrt.ECA))/sd(ch20rsc$sqrt.ECA)

#normalize CPD 2 - square root transformation (ie. sqrt(x))
ch20rsc$sqrt.CPD=sqrt(ch20rsc$disturbedarea_prct_cs)
ch20rsc$sqrt.CPD.std=(ch20rsc$sqrt.CPD-mean(ch20rsc$sqrt.CPD))/sd(ch20rsc$sqrt.CPD)

ch20rsc$npgo.std=(ch20rsc$npgo-mean(ch20rsc$npgo))/sd(ch20rsc$npgo)
ch20rsc$sst.std=(ch20rsc$spring_ersst-mean(ch20rsc$spring_ersst))/sd(ch20rsc$spring_ersst)

cu = distinct(ch20rsc,.keep_all = T)

cu_n = as.numeric(factor(cu$CU))

ch20rsc$CU_n <- cu_n

# make CU_NAME values Title case instead of all caps
ch20rsc$CU_name <- str_to_title(ch20rsc$CU_NAME)

# glimpse(ch20rsc)

max_eca_df <- ch20rsc %>% 
  select(River, River_n,CU, CU_n, CU_name, ECA_age_proxy_forested_only) %>%
  group_by(River) %>%
  summarize(River_n = first(River_n),
            River = first(River),
            CU = first(CU),
            CU_n = first(CU_n),
            CU_name = first(CU_name),
            eca_max = 100*max(ECA_age_proxy_forested_only, na.rm =TRUE)) %>% 
  mutate(eca_level = case_when(eca_max < 12 ~ 'low',
                               eca_max >= 12 & eca_max < 24 ~ 'medium',
                               eca_max >= 24 ~ 'high'))

max_cpd_df <- ch20rsc %>% 
  select(River, River_n,CU, CU_n, CU_name, disturbedarea_prct_cs) %>%
  group_by(River) %>% 
  summarize(River_n = first(River_n),
            River = first(River),
            CU = first(CU),
            CU_n = first(CU_n),
            CU_name = first(CU_name),
            cpd_max = max(disturbedarea_prct_cs, na.rm = TRUE))

ric_chm_eca_ocean_covariates_logR=read.csv(here('stan models','outs','posterior',
                                                'ric_chm_eca_ocean_covariates_logR_long_chain.csv'),check.names=F)

ric_chm_cpd_ocean_covariates_logR=read.csv(here('stan models','outs','posterior',
                                                'ric_chm_cpd_ocean_covariates_logR_long_chain.csv'),check.names=F)

md_watersheds <- ch20rsc %>% 
  select(River, CU) %>% 
  filter(CU == "CM-8") %>% 
  unique()

```


```{r}


# Pink --------------------------------------------------------------------



pk10r_e <- read.csv(here("origional-ecofish-data-models","Data","Processed","pke_SR_10_hat_yr_w_ersst.csv"))

#odd year pinks
pk10r_o <- read.csv(here("origional-ecofish-data-models","Data","Processed","pko_SR_10_hat_yr_w_ersst.csv"))

options(mc.cores=8)

# Pink salmon - even/odd croodlines #####
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=='950-169400-00000-00000-0000-0000-000-000-000-000-000-000','SALMON RIVER 2',pk10r_o$River)
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=='915-765500-18600-00000-0000-0000-000-000-000-000-000-000','HEAD CREEK 2',pk10r_o$River)
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=='915-488000-41400-00000-0000-0000-000-000-000-000-000-000','WINDY cAY CREEK 2',pk10r_o$River)
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=="915-486500-05300-00000-0000-0000-000-000-000-000-000-000",'LAGOON CREEK 2',pk10r_o$River)
pk10r_o=pk10r_o[order(factor(pk10r_o$River),pk10r_o$BroodYear),]
rownames(pk10r_o)=seq(1:nrow(pk10r_o))

pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=='950-169400-00000-00000-0000-0000-000-000-000-000-000-000','SALMON RIVER 2',pk10r_e$River)
pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=='915-765500-18600-00000-0000-0000-000-000-000-000-000-000','HEAD CREEK 2',pk10r_e$River)
pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=='915-488000-41400-00000-0000-0000-000-000-000-000-000-000','WINDY cAY CREEK 2',pk10r_e$River)
pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=="915-486500-05300-00000-0000-0000-000-000-000-000-000-000",'LAGOON CREEK 2',pk10r_e$River)
pk10r_e=pk10r_e[order(factor(pk10r_e$River),pk10r_e$BroodYear),]
rownames(pk10r_e)=seq(1:nrow(pk10r_e))


#normalize ECA 2 - square root transformation (ie. sqrt(x))
pk10r_o$sqrt.ECA=sqrt(pk10r_o$ECA_age_proxy_forested_only)
pk10r_o$sqrt.ECA.std=(pk10r_o$sqrt.ECA-mean(pk10r_o$sqrt.ECA))/sd(pk10r_o$sqrt.ECA)

#normalize CPD 2 - square root transformation (ie. sqrt(x))
pk10r_o$sqrt.CPD=sqrt(pk10r_o$disturbedarea_prct_cs)
pk10r_o$sqrt.CPD.std=(pk10r_o$sqrt.CPD-mean(pk10r_o$sqrt.CPD))/sd(pk10r_o$sqrt.CPD)

#normalize ECA 2 - square root transformation (ie. sqrt(x))
pk10r_e$sqrt.ECA=sqrt(pk10r_e$ECA_age_proxy_forested_only)
pk10r_e$sqrt.ECA.std=(pk10r_e$sqrt.ECA-mean(pk10r_e$sqrt.ECA))/sd(pk10r_e$sqrt.ECA)

#normalize CPD 2 - square root transformation (ie. sqrt(x))
pk10r_e$sqrt.CPD=sqrt(pk10r_e$disturbedarea_prct_cs)
pk10r_e$sqrt.CPD.std=(pk10r_e$sqrt.CPD-mean(pk10r_e$sqrt.CPD))/sd(pk10r_e$sqrt.CPD)


#standardize npgo
pk10r_o$npgo.std=(pk10r_o$npgo-mean(pk10r_o$npgo))/sd(pk10r_o$npgo)
pk10r_e$npgo.std=(pk10r_e$npgo-mean(pk10r_e$npgo))/sd(pk10r_e$npgo)

# pk10r_o$sst.std = (pk10r_o$spring_lighthouse_temperature-mean(pk10r_o$spring_lighthouse_temperature))/sd(pk10r_o$spring_lighthouse_temperature)
# pk10r_e$sst.std = (pk10r_e$spring_lighthouse_temperature-mean(pk10r_e$spring_lighthouse_temperature))/sd(pk10r_e$spring_lighthouse_temperature)

pk10r_o$sst.std = (pk10r_o$spring_ersst-mean(pk10r_o$spring_ersst))/sd(pk10r_o$spring_ersst)
pk10r_e$sst.std = (pk10r_e$spring_ersst-mean(pk10r_e$spring_ersst))/sd(pk10r_e$spring_ersst)


pk10r_o$escapement.t_1=pk10r_e$Spawners[match(paste(pk10r_o$WATERSHED_CDE,pk10r_o$BroodYear-1),paste(pk10r_e$WATERSHED_CDE,pk10r_e$BroodYear))]
pk10r_e$escapement.t_1=pk10r_o$Spawners[match(paste(pk10r_e$WATERSHED_CDE,pk10r_e$BroodYear-1),paste(pk10r_o$WATERSHED_CDE,pk10r_o$BroodYear))]

pk10r_o$Broodline='Odd'
pk10r_e$Broodline='Even'

L_o=pk10r_o%>%group_by(River)%>%summarize(l=n(),by=min(BroodYear),tmin=(min(BroodYear)-min(pk10r_o$BroodYear))/2+1,tmax=(max(BroodYear)-min(pk10r_o$BroodYear))/2)
L_e=pk10r_e%>%group_by(River)%>%summarize(l=n(),by=min(BroodYear),tmin=(min(BroodYear)-min(pk10r_e$BroodYear))/2+1,tmax=(max(BroodYear)-min(pk10r_e$BroodYear))/2)
L_o$River2=paste(L_o$River,'Odd',sep='_')
L_e$River2=paste(L_e$River,'Even',sep='_')
L_all=rbind(L_e,L_o)
L_all=L_all[order(factor(L_all$River2)),]

pk10r_o$ii=as.numeric(factor(pk10r_o$BroodYear))
pk10r_e$ii=as.numeric(factor(pk10r_e$BroodYear))

pk10r=rbind(pk10r_e,pk10r_o)
pk10r$River2=paste(pk10r$River,pk10r$Broodline,sep='_')
pk10r=pk10r[order(factor(pk10r$River2),pk10r$BroodYear),]

#extract max S for priors on capacity & eq. recruitment
smax_prior=pk10r%>%group_by(River2) %>%summarize(m.s=max(Spawners),m.r=max(Recruits))

#ragged start and end points for each SR series
# N_s=rag_n(pk10r$River2)

#cus by stock
cu1=distinct(pk10r,CU,.keep_all = T)
cu2=distinct(pk10r,River,.keep_all = T)
cu3=distinct(pk10r,River2,.keep_all = T)

pk10r$River_n <- as.numeric(factor(pk10r$River))
pk10r$River_n2 <- as.numeric(factor(pk10r$River2))
pk10r$CU_name <- pk10r$CU_NAME

max_eca_pink_df <- pk10r %>% 
  select(River2, River, River_n, CU, ECA_age_proxy_forested_only) %>%
  group_by(River) %>%
  summarize(River = first(River),
            River_n = first(River_n),
            CU = first(CU),
            eca_max = 100*max(ECA_age_proxy_forested_only, na.rm =TRUE)) %>% 
  mutate(eca_level = case_when(eca_max < 12 ~ 'low',
                               eca_max >= 12 & eca_max < 24 ~ 'medium',
                               eca_max >= 24 ~ 'high'))

max_cpd_pink_df <- pk10r %>%
  select(River2, River, River_n,  CU, disturbedarea_prct_cs) %>%
  group_by(River) %>% 
  summarize(River = first(River),
            River_n = first(River_n),
            CU = first(CU),
            cpd_max = max(disturbedarea_prct_cs, na.rm = TRUE))

md_watersheds_pink1 <- pk10r %>% 
  select(River, CU, River2, Broodline) %>% 
  filter(CU == "PKE-4" | CU == "PKO-7"| CU == "PKO-8") %>%
  unique()

#look at rivers in common between pop_sheds2 and md_watersheds_pink1

md_watersheds_pink <- md_watersheds_pink1 %>% 
  filter(River %in% pop_sheds2$River)

md_watersheds_total <- md_watersheds %>% 
  rename(CU_chum = CU) %>%
  full_join(md_watersheds_pink %>% select(Broodline, River, CU) %>% 
              pivot_wider(names_from = Broodline, values_from = CU, names_prefix = "CU_pink_"), by = 'River')


ric_pk_cpd_ersst_long_chain <- read.csv(here('stan models','outs','posterior',"ric_pk_cpd_st_noac_ocean_covariates_logR_long_chain_sigma_vector.csv"),
                                        check.names = FALSE)

ric_pk_eca_ersst_long_chain <- read.csv(here('stan models','outs','posterior',"ric_pk_eca_st_noac_ocean_covariates_logR_long_chain_sigma_vector.csv"),
                                        check.names = FALSE)



```



```{r fig.height=12, fig.width=10}
ggplot() +
  geom_sf(data = bc_boundary, fill = "gray90", color = alpha("slategray",0.1), linewidth = 0.5) +
  # geom_sf(data = Canada, fill = "grey90", color = NA) +
  # geom_sf(data = USA, fill = "grey90", color = NA) +
  # Regional colors layer
  geom_sf(data = pop_sheds2, 
          aes(fill = CPD*100), color = "gray90", linewidth = 0.2)  +
  geom_sf(data = md_territory, fill = "transparent", color = "darkred", linewidth = 0.8) +
  #label watersheds with River
  #arrow to the watershed
  geom_sf_label_repel(data =pop_sheds2 %>% filter(River %in% md_watersheds_total$River | startsWith(River, "KINGCOME") ) , aes(label = River),
                size = 3, color = "black", alpha = 0.7, 
                # family = "ArcherPro Book",
                # hjust = 0,
                label.padding = unit(0.15, "lines"),
                # point.padding = unit(2, "lines"),
                # direction = "both",
                # segment.size = 0.2,
                # min.segment.length = unit(1, "inches"),
                # xlim = c(st_bbox(md_territory)$xmax,b["xmax"]+90000),
                # ylim = c(b["ymin"]-150000 , b["ymax"]+100000),
                max.overlaps = 10,
                force        = 0.5,
                nudge_x      = st_bbox(md_territory)$xmax/20,
                direction    = "y",
                hjust        = 0
                )+
                # nudge_x = 70000, nudge_y = -20000) +
  # 
  # # Plot Window
  coord_sf(crs = st_crs(pop_sheds2),
           xlim = c(b["xmin"]-100000, b["xmax"]+100000 ) ,
           ylim = c(b["ymin"]-150000 , b["ymax"]+100000)) +

  # scale_color_manual("MD territory", values = "darkred") +
  scale_fill_gradient2(name = 'Cumulative Disturbed\nArea (CDA) (%)', guide = guide_colorbar(ticks = FALSE, barheight = 5),
                       low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 50) +
  # scale_color_gradient2(name = 'CPD',
  #                       low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 50) +
  labs(x = "", y = "", color = "", fill = "") +
  theme(panel.grid.major = element_line(colour = "aliceblue", linetype = "dashed", 
                                        size = 0.5), 
        panel.background = element_rect(fill = "aliceblue"), 
        panel.border = element_rect(fill = NA, color = NA),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        base_family = "ArcherPro Book",
        legend.position = c(0.1, 0.9),
        # legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.font = "ArcherPro Book",
        legend.key.size = unit(0.8, "cm"),
        legend.key.spacing.y = unit(0.5, "cm"),
        legend.key.width = unit(0.5, "cm"),
        legend.key.height = unit(0.5, "cm"),
        legend.background = element_rect(fill = "transparent", size = 0.5)
  ) 
  # labs(x = "", y = "", color = "", fill = "") +
  # # Spatial annotation
  # ggspatial::annotation_scale(
  #   location = "bl",
  #   bar_cols = c("black", "white"),
  #   text_family = "ArcherPro Book"
  # ) +
  # ggspatial::annotation_north_arrow(
  #   location = "tr", which_north = "true",
  #   # pad_x = unit(0.4, "in"), pad_y = unit(0.4, "in"),
  #   style = ggspatial::north_arrow_nautical(
  #     fill = c("black", "white"),
  #     line_col = "black",
  #     text_family = "ArcherPro Book"
  #   )
  # ) 
  # inset_element(wld_map, left = 0.05, bottom = 0.1, right = 0.3, top = 0.35, align_to = "plot")
  # inset_element(bc, left = 0.0, bottom = 0.0, right = 0.45, top = 0.45, align_to = "plot")
# 

```





```{r}

plot_all_effects_river_together <- function(posterior1 = ric_chm_cpd_ocean_covariates_logR,
                                            river_name,
                                            river,
                                            effect1 = "cpd",
                                            effect2 = "sst",
                                            effect3 = "npgo",
                                            species = "chum", 
                                            xlim = c(-0.5, 0.5)){
  
  
  
  
  posterior_df <- posterior1 %>%
    select(starts_with('b_for_rv'),starts_with('b_sst_rv'),starts_with('b_npgo_rv')) %>%
    pivot_longer(cols = everything(),
                 names_to = c('Effect','River'),
                 names_pattern = 'b_(.*)_rv(.*)',
                 values_to = "coefficient") %>%
    
    
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) 
  
  
  if(effect1 == "cpd"){
    posterior_df_river <- posterior_df %>% filter(River_n == river) %>% 
      mutate(Effect = case_when(Effect == "for" ~ "CDA",
                                Effect == "sst" ~ "SST",
                                Effect == "npgo" ~ "NPGO"))
  } else if(effect1 == "eca"){
    posterior_df_river <- posterior_df %>% filter(River_n == river) %>% 
      mutate(Effect = case_when(Effect == "for" ~ "ECA",
                                Effect == "sst" ~ "SST",
                                Effect == "npgo" ~ "NPGO"))
  }
  
  

  
  #color by river
  plot1 <- ggplot() +
    stat_density(data= posterior_df_river, aes(coefficient,#!!sym(forestry), 
                                               
                                               group = Effect, 
                                               color = Effect,
                                               fill = Effect),
                 geom = 'area', position = 'identity', 
                 alpha = 0.4, linewidth = 0.8) +
    
    geom_vline(xintercept = 0, color = 'slategray', linewidth = 0.8) +
    geom_vline(aes(xintercept = median(posterior_df_river$coefficient[posterior_df_river$Effect == "CDA"]), 
               color = "CDA"), linetype = "dashed", linewidth = 0.8) +
    geom_vline(aes(xintercept = median(posterior_df_river$coefficient[posterior_df_river$Effect == "SST"]), 
               color = "SST"), linetype = "dashed", linewidth = 0.8) +
    geom_vline(aes(xintercept = median(posterior_df_river$coefficient[posterior_df_river$Effect == "NPGO"]),
               color = "NPGO"), linetype = "dashed", linewidth = 0.8) +
    labs(x = "Standardized coefficients", y = "Posterior density", title = river_name) +
    xlim(xlim[1], xlim[2]) +
    scale_color_manual(name = "",
                       values = c("ECA" = "#ADcCA5", 
                                  "CDA" = "#ADcCA5",
                                  "SST" = "#C78c63",
                                  "NPGO" = "#829Dc6")) +
    scale_fill_manual(name = "",
                      values = c("ECA" = "#ADcCA5", 
                                 "CDA" = "#ADcCA5",
                                 "SST" = "#C78c63",
                                 "NPGO" = "#829Dc6")) +
    # scale_color +
    # geom_density(aes(posterior$b_for), color = 'black', linewidth = 1.2, alpha = 0.2)+
    #vline at the median value of the posterior
    theme_classic()+
    theme(legend.position = c(0.8,0.9),
          legend.background = element_rect(fill = alpha('white', 0.5)),
          legend.text = element_text(size = 7),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          plot.title = element_blank()
    )
  
  
  
  return(plot1)
}


plot_recruitment_change_river_together <- function(posterior1 = ric_chm_cpd_ocean_covariates_logR,
                                                   posterior2 = ric_chm_eca_ocean_covariates_logR,
                                                   river_name = "CARNATION CREEK",  
                                                   effect1 = "cpd",
                                                   effect2 = "eca",
                                                   species = "chum", 
                                                   model1 = "CPD",
                                                   model2 = "ECA",
                                                   hd = FALSE){
  
  
  if(species == "chum"){
    df <- ch20rsc 
    river_data <- ch20rsc %>% filter(River == river_name)
    river <- river_data$River_n[1]
    # df$sst.std <- (ch20rsc$spring_ersst-mean(ch20rsc$spring_ersst))/sd(ch20rsc$spring_ersst)
    
  } else if(species == "pink"){
    df <- pk10r
    river_data <- pk10r %>% filter(River == river_name)
    river <- river_data$River_n[1]
    # df$sst.std <- (pk10r$spring_ersst-mean(pk10r$spring_ersst))/sd(pk10r$spring_ersst)
  }
  
  posterior_df <- posterior1 %>%
    select(starts_with(paste0('b_for_rv[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_for_rv',
                 values_to = "forestry") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  posterior_df2 <- posterior2 %>% 
    select(starts_with(paste0('b_for_rv[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_for_rv',
                 values_to = "forestry") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  
  
  
  eca <- seq(0,1,length.out=100)
  
  eca_sqrt <- sqrt(eca)
  
  eca_sqrt_std <- (eca_sqrt-mean(eca_sqrt))/sd(eca_sqrt)
  
  cpd <- seq(0,100,length.out=100)
  
  cpd_sqrt <- sqrt(cpd)
  
  cpd_sqrt_std <- (cpd_sqrt-mean(cpd_sqrt))/sd(cpd_sqrt)
  
  
  
  
  no_eca <- min(eca_sqrt_std)
  
  no_cpd <- min(cpd_sqrt_std)
  
  
  
  # need to change b_rv to posterior 1 and posterior 2 and then make figure
  
  productivity_cpd <- (exp(as.matrix(posterior_df[,1])%*%
                             (cpd_sqrt_std-no_cpd)))*100 - 100
  
  productivity_eca <- (exp(as.matrix(posterior_df2[,1])%*%
                             (eca_sqrt_std-no_eca)))*100 - 100
  
  
  productivity_cpd_df <- data.frame(productivity_cpd_median = apply(productivity_cpd,2,median),
                                    productivity_cpd_025 = apply(productivity_cpd,2,quantile,c(0.025), 
                                                                 row.names = c("q025")),
                                    productivity_cpd_975 = apply(productivity_cpd,2,quantile,c(0.975),
                                                                 row.names = c("q975")),
                                    productivity_cpd_100 = apply(productivity_cpd,2,quantile,c(0.1),
                                                                 row.names = c("q100")),
                                    productivity_cpd_900 = apply(productivity_cpd,2,quantile,c(0.9),
                                                                 row.names = c("q900")),
                                    productivity_cpd_250 = apply(productivity_cpd,2,quantile,c(0.25),
                                                                 row.names = c("q250")),
                                    productivity_cpd_750 = apply(productivity_cpd,2,quantile,c(0.75),
                                                                 row.names = c("q750")),
                                    
                                    
                                    productivity_cpd_025_hd = apply(productivity_cpd,2,HDInterval::hdi, credMass = 0.95)[1,],
                                    productivity_cpd_975_hd = apply(productivity_cpd,2,HDInterval::hdi, credMass = 0.95)[2,],
                                    productivity_cpd_100_hd = apply(productivity_cpd,2,HDInterval::hdi, credMass = 0.8)[1,],
                                    productivity_cpd_900_hd = apply(productivity_cpd,2,HDInterval::hdi, credMass = 0.8)[2,],
                                    productivity_cpd_50_lower_hd = apply(productivity_cpd,2,HDInterval::hdi, credMass = 0.5)[1,],
                                    productivity_cpd_50_upper_hd = apply(productivity_cpd,2,HDInterval::hdi, credMass = 0.5)[2,],
                                    
                                    
                                    
                                    cpd_sqrt_std = cpd_sqrt_std,
                                    cpd = cpd,
                                    max_cpd = max(river_data$disturbedarea_prct_cs),
                                    max_sqrt_cpd = max(river_data$sqrt.CPD),
                                    model = "CPD"
  )
  
  
  productivity_eca_df <- data.frame(productivity_eca_median = apply(productivity_eca,2,median),
                                    productivity_eca_025 = apply(productivity_eca,2,quantile,c(0.025), 
                                                                 row.names = c("q025")),
                                    productivity_eca_975 = apply(productivity_eca,2,quantile,c(0.975),
                                                                 row.names = c("q975")),
                                    productivity_eca_100 = apply(productivity_eca,2,quantile,c(0.1),
                                                                 row.names = c("q100")),
                                    productivity_eca_900 = apply(productivity_eca,2,quantile,c(0.9),
                                                                 row.names = c("q900")),
                                    productivity_eca_250 = apply(productivity_eca,2,quantile,c(0.25),
                                                                 row.names = c("q250")),
                                    productivity_eca_750 = apply(productivity_eca,2,quantile,c(0.75),
                                                                 row.names = c("q750")),
                                    
                                    productivity_eca_025_hd = apply(productivity_eca,2,HDInterval::hdi, credMass = 0.95)[1,],
                                    productivity_eca_975_hd = apply(productivity_eca,2,HDInterval::hdi, credMass = 0.95)[2,],
                                    productivity_eca_100_hd = apply(productivity_eca,2,HDInterval::hdi, credMass = 0.8)[1,],
                                    productivity_eca_900_hd = apply(productivity_eca,2,HDInterval::hdi, credMass = 0.8)[2,],
                                    productivity_eca_50_lower_hd = apply(productivity_eca,2,HDInterval::hdi, credMass = 0.5)[1,],
                                    productivity_eca_50_upper_hd = apply(productivity_eca,2,HDInterval::hdi, credMass = 0.5)[2,],
                                    
                                    eca_sqrt_std = eca_sqrt_std,
                                    eca = eca,
                                    max_eca = max(river_data$ECA_age_proxy_forested_only),
                                    max_sqrt_eca = max(river_data$sqrt.ECA),
                                    model = "ECA"
  )
  
  
  plot1 <- ggplot(productivity_cpd_df) +
      geom_line(aes(x = cpd, y = productivity_cpd_median, group = 1,
                    color = "median"),alpha=0.9, linewidth = 0.8) +
      geom_ribbon(aes(x = cpd, ymin = productivity_cpd_025, ymax = productivity_cpd_975, fill = "95% credible interval"),
                  alpha = 0.2) +
      geom_ribbon(aes(x = cpd, ymin = productivity_cpd_100, ymax = productivity_cpd_900, fill = "80% credible interval"),
                  alpha = 0.4) +
      geom_ribbon(aes(x = cpd, ymin = productivity_cpd_250, ymax = productivity_cpd_750, fill = "50% credible interval"),
                  alpha = 0.6) +
      
      geom_segment(aes(x = unique(productivity_cpd_df$max_cpd), 
                       xend = unique(productivity_cpd_df$max_cpd), 
                       y = -100, 
                       yend = productivity_cpd_median[which.min(abs(cpd - unique(productivity_cpd_df$max_cpd)))],
                       color = "gray"), 
                   linetype = "dashed", linewidth = 0.8) +
      # add horizontal line 
      geom_segment(aes(x = 0, 
                       xend = unique(productivity_cpd_df$max_cpd), 
                       y = productivity_cpd_median[which.min(abs(cpd - unique(productivity_cpd_df$max_cpd)))], 
                       yend = productivity_cpd_median[which.min(abs(cpd - unique(productivity_cpd_df$max_cpd)))],
                       color = "gray"), 
                   linetype = "dashed", linewidth = 0.8) +
      annotate("text",x = unique(productivity_cpd_df$max_cpd), 
               y = productivity_cpd_df$productivity_cpd_median[which.min(abs(cpd - unique(productivity_cpd_df$max_cpd)))],
               label = paste0("Max CDA: ",round(unique(productivity_cpd_df$max_cpd),1),"%\n",
                              "Median change: ",round(productivity_cpd_df$productivity_cpd_median[which.min(abs(cpd - unique(productivity_cpd_df$max_cpd)))],1),"%"),
               vjust = -0.5, color = "black", size = 2, hjust = 0
      ) +
      
      scale_color_manual(name = "Model",
                         values = c("ECA model" = '#A2C5AC', 
                                    "median" = '#A2C5AC')) +
      scale_fill_manual(name = "Model",
                        values = c("ECA 95% credible interval" = '#A2C5AC', 
                                   "ECA 80% credible interval" = '#A2C5AC',
                                   "95% credible interval" = '#A2C5AC', 
                                   "80% credible interval" = '#A2C5AC',
                                   "50% credible interval" = '#A2C5AC')) +
      ylim(-100,100) +
      scale_x_continuous(n.breaks = 5) +
      labs(x = "CDA (%)",
           y = "Change in recruitment (%)") +
      theme_classic() +
      theme(legend.position = "none",
            legend.title = element_blank(),
            legend.key.size = unit(0.5, "cm"),
            legend.key.width = unit(0.5, "cm"),
            legend.spacing.y = unit(0.1, "cm"),
            legend.key.height = unit(0.5, "cm"),
            axis.title.x = element_text(size = 8),
            axis.title.y = element_text(size = 8),
            axis.text.x = element_text(size = 8),
            axis.text.y = element_text(size = 8),
            plot.title = element_text(size = 10, hjust = 0.5))+
      guides(color = guide_legend(override.aes = list(alpha = 1, linewidth = 1.5)))
    
    plot2 <- ggplot(productivity_eca_df)+
      geom_line(aes(x = eca, y = productivity_eca_median, group = 1,
                    color = "median"),alpha=0.9, linewidth = 0.8) +
      geom_ribbon(aes(x = eca, ymin = productivity_eca_025, ymax = productivity_eca_975, fill = "95% credible interval"),
                  alpha = 0.2) +
      geom_ribbon(aes(x = eca, ymin = productivity_eca_100, ymax = productivity_eca_900, fill = "80% credible interval"),
                  alpha = 0.4) +
      geom_ribbon(aes(x = eca, ymin = productivity_eca_250, ymax = productivity_eca_750, fill = "50% credible interval"),
                  alpha = 0.6) +
      #add vertical line at max eca - max height should be value of productivity eca median
      geom_segment(aes(x = unique(productivity_eca_df$max_eca), 
                       xend = unique(productivity_eca_df$max_eca), 
                       y = -100, 
                       yend = productivity_eca_median[which.min(abs(eca - unique(productivity_eca_df$max_eca)))],
                       color = "gray"), 
                   linetype = "dashed", linewidth = 0.8) +
      # add horizontal line 
      geom_segment(aes(x = 0, 
                       xend = unique(productivity_eca_df$max_eca), 
                       y = productivity_eca_median[which.min(abs(eca - unique(productivity_eca_df$max_eca)))], 
                       yend = productivity_eca_median[which.min(abs(eca - unique(productivity_eca_df$max_eca)))],
                       color = "gray"), 
                   linetype = "dashed", linewidth = 0.8) +
      annotate("text",x = unique(productivity_eca_df$max_eca), 
               y = productivity_eca_df$productivity_eca_median[which.min(abs(eca - unique(productivity_eca_df$max_eca)))],
               label = paste0("Max ECA: ",round(unique(productivity_eca_df$max_eca),2),"\n",
                              "Median change: ",round(productivity_eca_df$productivity_eca_median[which.min(abs(eca - unique(productivity_eca_df$max_eca)))],1),"%"),
               vjust = -0.5, color = "black", size = 2, hjust = 0
      ) +
      
      
      scale_color_manual(values = c("median" = '#7F6A93', 
                                    "CPD model" = '#7F6A93')) +
      scale_fill_manual(values = c("95% credible interval" = '#7F6A93', 
                                   "80% credible interval" = '#7F6A93',
                                   "50% credible interval" = '#7F6A93',
                                   "CPD model 95% credible interval" = '#7F6A93', 
                                   "CPD model 80% credible interval" = '#7F6A93')) +
      ylim(-100,100) +
      scale_x_continuous(n.breaks = 5) +
      labs(x = "ECA",
           y = "Change in recruitment (%)") +
      theme_classic() +
      theme(legend.position = "inside",
            legend.justification = c("right", "top"),
            legend.byrow = FALSE,
            legend.title = element_blank(),
            # legend.key.size = unit(0.5, "cm"),
            legend.key.width = unit(0.5, "cm"),
            legend.spacing.y = unit(0, "cm"),
            legend.key.height = unit(0.2, "cm"),
            legend.text = element_text(size = 6),
            axis.title.x = element_text(size = 8),
            axis.title.y = element_text(size = 8),
            axis.text.x = element_text(size = 8),
            axis.text.y = element_text(size = 8),
            plot.title = element_text(size = 10, hjust = 0.5))+
      guides(color = guide_legend(override.aes = list(alpha = 1, linewidth = 1.5)))
  
  
 
  
  return(plot1+plot2 + plot_layout(axes = 'collect') +
           plot_annotation(title = str_to_title(river_name),tag_level = 'A')&
           theme(plot.tag.position = c(0.05, 1),
                 plot.tag = element_text(size = 10, hjust = 0, vjust = 0, face = "bold")))
  
}


plot_both_forestry_effects_river_together <- function(posterior1 = ric_chm_cpd_ersst,
                                                posterior2 = ric_chm_eca_ersst,
                                                river,
                                                effect1 = "cpd",
                                                effect2 = "eca",
                                                species = "chum", 
                                                model1 = "CPD",
                                                model2 = "ECA",
                                                xlim = c(-2, 2)){
  
  
 
       
  posterior_df <- posterior1 %>%
    select(starts_with('b_for_rv')) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_for_rv',
                 values_to = "forestry") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) 
  
  posterior_df2 <- posterior2 %>% 
    select(starts_with('b_for_rv')) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_for_rv',
                 values_to = "forestry") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River)
  
  
  posterior_df_river1 <- posterior_df %>% filter(River_n == river) %>% 
    mutate(model = model1)
  
  posterior_df_river2 <- posterior_df2 %>% filter(River_n == river) %>% 
    mutate(model = model2)
  
  posterior_df_river <- posterior_df_river1 %>% 
    bind_rows(posterior_df_river2)
  
  #color by river
  plot1 <- ggplot() +
    stat_density(data= posterior_df_river, aes(forestry,#!!sym(forestry), 
      
                                               group = model, 
                                               color = model,
                                               fill = model),
                 geom = 'area', position = 'identity', 
                 alpha = 0.4, linewidth = 0.8) +
    
    geom_vline(xintercept = 0, color = 'slategray', linewidth = 0.8) +
    labs(x = "Standardized coefficients", y = "Posterior density") +
    xlim(xlim[1], xlim[2]) +
    scale_color_manual(name = "Model",
                       values = c("ECA" = '#7F6A93', 
                                  "CPD" = '#A2C5AC')) +
    scale_fill_manual(name = "Model",
                       values = c("ECA" = '#7F6A93', 
                                  "CPD" = '#A2C5AC')) +
    # scale_color +
    # geom_density(aes(posterior$b_for), color = 'black', linewidth = 1.2, alpha = 0.2)+
    #vline at the median value of the posterior
    theme_classic()+
    theme(legend.position = 'right',
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          plot.title = element_text(size = 14, hjust = 0.5)
          )
  
  
  
  return(plot1)
}



plot_recruit_spawner_river_new <- function(species = "chum", river_name,  posterior){
  
  # river_data <- df %>% filter(River_n == river)
  
  if(species == "chum"){
    df <- ch20rsc 
    river_data <- ch20rsc %>% filter(River == river_name)
    river <- river_data$River_n[1]
    # df$sst.std <- (ch20rsc$spring_ersst-mean(ch20rsc$spring_ersst))/sd(ch20rsc$spring_ersst)
    
  } else if(species == "pink"){
    df <- pk10r
    river_data <- pk10r %>% filter(River == river_name)
    river <- river_data$River_n2[1]
    # df$sst.std <- (pk10r$spring_ersst-mean(pk10r$spring_ersst))/sd(pk10r$spring_ersst)
  }
  
  if(species == "chum"){
    posterior_rv_b_for <- posterior %>% 
      select(starts_with('b_for_rv')) %>%
      select(ends_with(paste0("[",river,"]")))
    
    posterior_rv_alpha_j <- posterior %>% 
      select(starts_with('alpha_j')) %>%
      select(ends_with(paste0("[",river,"]")))
    
    posterior_rv_S_max <- posterior %>% 
      select(starts_with('Smax')) %>%
      select(ends_with(paste0("[",river,"]")))
    
    
  } else if(species == "pink"){
    
    river_wo_broodline <- river_data$River_n
    river_w_broodline <- river_data$River_n2
    
    posterior_rv_b_for <- posterior %>% 
      select(starts_with('b_for_rv')) %>%
      select(ends_with(paste0("[",river_wo_broodline,"]")))
    
    posterior_rv_alpha_j <- posterior %>% 
      select(starts_with('alpha_j')) %>%
      select(ends_with(paste0("[",river_w_broodline,"]")))
    
    posterior_rv_S_max <- posterior %>% 
      select(starts_with('Smax')) %>%
      select(ends_with(paste0("[",river_w_broodline,"]")))
    
    
    
  }
  
  
  spawners_predicted <- seq(0, max(river_data$Spawners), length.out = 100)
  
  # calculate recruit prediction
  
  low_cpd <- min(river_data$sqrt.CPD.std)
  high_cpd <- max(river_data$sqrt.CPD.std)
  # avg_cpd <- mean(river_data$sqrt.CPD.std)
  mid_cpd <- min(river_data$sqrt.CPD.std) + (max(river_data$sqrt.CPD.std) - min(river_data$sqrt.CPD.std))/2
  
  mid_cpd_real <- min(river_data$disturbedarea_prct_cs) + (max(river_data$disturbedarea_prct_cs) - min(river_data$disturbedarea_prct_cs))/2
  
  
  recruits_predicted_low_cpd <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*low_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, median))*spawners_predicted
  
  recruits_predicted_high_cpd <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*high_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, median))*spawners_predicted
  
  
  recruits_predicted_low_cpd_lower <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*low_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.025)))*spawners_predicted
  
  recruits_predicted_low_cpd_upper <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*low_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.975)))*spawners_predicted
  
  recruits_predicted_high_cpd_lower <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*high_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.025)))*spawners_predicted
  
  recruits_predicted_high_cpd_upper <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*high_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.975)))*spawners_predicted
  
  
  
  #make dataframe
  
  prediction_df <- data.frame(spawners = spawners_predicted,
                              
                              recruits_low_cpd = recruits_predicted_low_cpd,
                              recruits_high_cpd = recruits_predicted_high_cpd,
                              recruits_low_cpd_lower = recruits_predicted_low_cpd_lower,
                              recruits_low_cpd_upper = recruits_predicted_low_cpd_upper,
                              recruits_high_cpd_lower = recruits_predicted_high_cpd_lower,
                              recruits_high_cpd_upper = recruits_predicted_high_cpd_upper)
  
  
  
  
  
  
  
  #plot the time varying productivity vs year, with log(R/S) data
  
  
  
  
  
  #plot recruit vs spawner as points
  
  p1 <- ggplot() +
    geom_point(data = river_data,aes(x = Spawners, y = Recruits, color = disturbedarea_prct_cs), alpha = 0.5, size = 2) +
    geom_line(data = prediction_df, aes(x = spawners, y = recruits_low_cpd), color = '#35978f', size = 1, alpha = 0.5) +
    geom_line(data = prediction_df, aes(x = spawners, y = recruits_high_cpd), color = '#bf812d', size = 1, alpha = 0.5) +
    # geom_line(data = prediction_df, aes(x = spawners, y = recruits), color = "black", size = 1, alpha = 0.5) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = recruits_low_cpd_lower, ymax = recruits_low_cpd_upper), fill ='#35978f', alpha = 0.1) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = recruits_high_cpd_lower, ymax = recruits_high_cpd_upper), fill ='#bf812d', alpha = 0.1) +
    #make y log scale
    # scale_y_log10() +
    labs(title = "", x = "Spawners", y = "Recruits") +
    # scale_color_manual(name = "CPD", values = c("Low" = '#35978f', "High" = '#bf812d')) +
    scale_color_gradient2(name = 'CDA (%)', guide = guide_colorbar(barwidth = 3, barheight = 0.5),
                          low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 20, n.breaks = 4) +
    theme_classic() +
    theme(legend.position = c(0.8,0.9),
          legend.background = element_rect(fill = alpha('white', 0.5)),
          legend.direction = "horizontal",
          legend.text = element_text(size = 7),
          legend.title = element_text(size = 8, vjust = 1, hjust = 1),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          plot.title = element_blank()
          # legend.key.width = unit(0.5, "cm"),
          # legend.key.height = unit(1, "lines"),
          # legend.spacing.y = unit(0.001, "cm")
    )
  
  
  # p3 log R/s vs spawners
  
  p2 <- ggplot(river_data) + 
    geom_point(aes(x = Spawners, y = log(Recruits/Spawners), color = disturbedarea_prct_cs), alpha = 0.5, size = 2) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_low_cpd/spawners_predicted)), color = '#35978f', size = 1, alpha = 0.5) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_high_cpd/spawners_predicted)), color = '#bf812d', size = 1, alpha = 0.5) +
    # geom_line(data = prediction_df, aes(x = spawners, y = log_RS), color = "black", size = 1, alpha = 0.5) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_low_cpd_lower/spawners_predicted), ymax = log(recruits_predicted_low_cpd_upper/spawners_predicted)), fill = "#35978f", alpha = 0.1) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_high_cpd_lower/spawners_predicted), ymax = log(recruits_predicted_high_cpd_upper/spawners_predicted)), fill = "#bf812d", alpha = 0.1) +
    labs(#title = "Ricker model with CPD, NPGO, ERSST", 
      x = "Spawners", y = TeX(r"($\log \left(\frac{Recruits}{Spawners}\right)$)")) +
    scale_color_gradient2(name = 'CDA (%)',
                          low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 20, guide = guide_colorbar(barwidth = 3, barheight = 0.5)) +
    theme_classic() +
    theme(legend.position = c(0.8,0.9),
          legend.background = element_rect(fill = alpha('white', 0.5)),
          legend.text = element_text(size = 7),
          legend.title = element_text(size = 8),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          plot.title = element_blank(),
          legend.key.width = unit(0.5, "cm"),
          legend.key.height = unit(1, "lines"),
          legend.spacing.y = unit(0.001, "cm")
    )
  
  p3 <- ggplot(river_data) + 
    geom_point(aes(x = Spawners, y = log(Recruits), color = disturbedarea_prct_cs), alpha = 0.5, size = 2) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_low_cpd)), color = '#35978f', size = 1, alpha = 0.5) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_high_cpd)), color = '#bf812d', size = 1, alpha = 0.5) +
    # geom_line(data = prediction_df, aes(x = spawners, y = log_RS), color = "black", size = 1, alpha = 0.5) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_low_cpd_lower), ymax = log(recruits_predicted_low_cpd_upper)), fill = "#35978f", alpha = 0.1) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_high_cpd_lower), ymax = log(recruits_predicted_high_cpd_upper)), fill = "#bf812d", alpha = 0.1) +
    labs(#title = "Ricker model with CPD, NPGO, ERSST", 
      x = "Spawners", y = TeX(r"($\log \left(Recruits\right)$)")) +
    scale_color_gradient2(name = 'CDA (%)',
                          low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 20)+
    theme_classic() +
    theme(legend.position = c(0.8,0.9),
          legend.background = element_rect(fill = alpha('white', 0.5)),
          legend.text = element_text(size = 7),
          legend.title = element_text(size = 8),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          plot.title = element_blank(),
          legend.key.width = unit(0.5, "cm"),
          legend.key.height = unit(1, "lines"),
          legend.spacing.y = unit(0.001, "cm")
    )
  
  
  
  
  
  
  return((p1))
}



plot_recruit_spawner_river_pink <- function(species = "pink", river_name,  posterior){
  
  # river_data <- df %>% filter(River_n == river)
  even_or_odd <- str_extract(river_name, "Even|Odd")
  
  df <- pk10r
  river_data <- pk10r %>% filter(River2 == river_name)
  
  # df$sst.std <- (pk10r$spring_ersst-mean(pk10r$spring_ersst))/sd(pk10r$spring_ersst)
  
  
  river_wo_broodline <- unique(river_data$River_n)
  river_w_broodline <- unique(river_data$River_n2)
  
  posterior_rv_b_for <- posterior %>% 
    select(starts_with('b_for_rv')) %>%
    select(ends_with(paste0("[",river_wo_broodline,"]")))
  
  posterior_rv_alpha_j <- posterior %>% 
    select(starts_with('alpha_j')) %>%
    select(ends_with(paste0("[",river_w_broodline,"]")))
  
  posterior_rv_S_max <- posterior %>% 
    select(starts_with('Smax')) %>%
    select(ends_with(paste0("[",river_w_broodline,"]")))
  
  # for(river in river_w_broodline_both){
  #   
  #   posterior_rv_alpha_j <- posterior %>% 
  #     select(starts_with('alpha_j')) %>%
  #     select(ends_with(paste0("[",river_w_broodline,"]")))
  #   
  #   posterior_rv_S_max <- posterior %>% 
  #     select(starts_with('Smax')) %>%
  #     select(ends_with(paste0("[",river_w_broodline,"]")))
  #   
  # }
  
  
  
  
  
  
  
  
  spawners_predicted <- seq(0, max(river_data$Spawners), length.out = 100)
  
  # calculate recruit prediction
  
  low_cpd <- min(river_data$sqrt.CPD.std)
  high_cpd <- max(river_data$sqrt.CPD.std)
  # avg_cpd <- mean(river_data$sqrt.CPD.std)
  mid_cpd <- min(river_data$sqrt.CPD.std) + (max(river_data$sqrt.CPD.std) - min(river_data$sqrt.CPD.std))/2
  
  mid_cpd_real <- min(river_data$disturbedarea_prct_cs) + (max(river_data$disturbedarea_prct_cs) - min(river_data$disturbedarea_prct_cs))/2
  
  
  recruits_predicted_low_cpd <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*low_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, median))*spawners_predicted
  
  recruits_predicted_high_cpd <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*high_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, median))*spawners_predicted
  
  
  recruits_predicted_low_cpd_lower <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*low_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.025)))*spawners_predicted
  
  recruits_predicted_low_cpd_upper <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*low_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.975)))*spawners_predicted
  
  recruits_predicted_high_cpd_lower <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*high_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.025)))*spawners_predicted
  
  recruits_predicted_high_cpd_upper <- exp(apply((matrix(posterior_rv_alpha_j[,1], ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1])) - as.matrix(1/posterior_rv_S_max)%*%spawners_predicted  + matrix(posterior_rv_b_for[,1]*high_cpd, ncol = length(spawners_predicted), nrow = length(posterior_rv_alpha_j[,1]))), 2, quantile, c(0.975)))*spawners_predicted
  
  
  
  #make dataframe
  
  prediction_df <- data.frame(spawners = spawners_predicted,
                              
                              recruits_low_cpd = recruits_predicted_low_cpd,
                              recruits_high_cpd = recruits_predicted_high_cpd,
                              recruits_low_cpd_lower = recruits_predicted_low_cpd_lower,
                              recruits_low_cpd_upper = recruits_predicted_low_cpd_upper,
                              recruits_high_cpd_lower = recruits_predicted_high_cpd_lower,
                              recruits_high_cpd_upper = recruits_predicted_high_cpd_upper)
  
  
  
  
  
  
  
  #plot the time varying productivity vs year, with log(R/S) data
  
  
  
  
  
  #plot recruit vs spawner as points
  
  p1 <- ggplot() +
    geom_point(data = river_data,aes(x = Spawners, y = Recruits, color = disturbedarea_prct_cs), alpha = 0.5, size = 2) +
    geom_line(data = prediction_df, aes(x = spawners, y = recruits_low_cpd), color = '#35978f', size = 1, alpha = 0.5) +
    geom_line(data = prediction_df, aes(x = spawners, y = recruits_high_cpd), color = '#bf812d', size = 1, alpha = 0.5) +
    # geom_line(data = prediction_df, aes(x = spawners, y = recruits), color = "black", size = 1, alpha = 0.5) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = recruits_low_cpd_lower, ymax = recruits_low_cpd_upper), fill ='#35978f', alpha = 0.1) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = recruits_high_cpd_lower, ymax = recruits_high_cpd_upper), fill ='#bf812d', alpha = 0.1) +
    #make y log scale
    # scale_y_log10() +
    labs(title = even_or_odd, x = "Spawners", y = "Recruits") +
    # scale_color_manual(name = "CPD", values = c("Low" = '#35978f', "High" = '#bf812d')) +
    scale_color_gradient2(name = 'CDA (%)', guide = guide_colorbar(barwidth = 3, barheight = 0.5),
                          low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 20, n.breaks = 4) +
    theme_classic() +
    theme(legend.position = c(0.8,0.9),
          legend.background = element_rect(fill = alpha('white', 0.5)),
          legend.direction = "horizontal",
          legend.text = element_text(size = 7),
          legend.title = element_text(size = 8, vjust = 1, hjust = 1),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          plot.title = element_text(size = 9)
          # legend.key.width = unit(0.5, "cm"),
          # legend.key.height = unit(1, "lines"),
          # legend.spacing.y = unit(0.001, "cm")
    )
  
  
  # p3 log R/s vs spawners
  
  p2 <- ggplot(river_data) + 
    geom_point(aes(x = Spawners, y = log(Recruits/Spawners), color = disturbedarea_prct_cs), alpha = 0.5, size = 2) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_low_cpd/spawners_predicted)), color = '#35978f', size = 1, alpha = 0.5) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_high_cpd/spawners_predicted)), color = '#bf812d', size = 1, alpha = 0.5) +
    # geom_line(data = prediction_df, aes(x = spawners, y = log_RS), color = "black", size = 1, alpha = 0.5) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_low_cpd_lower/spawners_predicted), ymax = log(recruits_predicted_low_cpd_upper/spawners_predicted)), fill = "#35978f", alpha = 0.1) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_high_cpd_lower/spawners_predicted), ymax = log(recruits_predicted_high_cpd_upper/spawners_predicted)), fill = "#bf812d", alpha = 0.1) +
    labs(#title = "Ricker model with CPD, NPGO, ERSST", 
      x = "Spawners", y = TeX(r"($\log \left(\frac{Recruits}{Spawners}\right)$)")) +
    scale_color_gradient2(name = 'CDA (%)',
                          low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 20, guide = guide_colorbar(barwidth = 3, barheight = 0.5)) +
    theme_classic() +
    theme(legend.position = c(0.8,0.9),
          legend.background = element_rect(fill = alpha('white', 0.5)),
          legend.text = element_text(size = 7),
          legend.title = element_text(size = 8),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          plot.title = element_blank(),
          legend.key.width = unit(0.5, "cm"),
          legend.key.height = unit(1, "lines"),
          legend.spacing.y = unit(0.001, "cm")
    )
  
  p3 <- ggplot(river_data) + 
    geom_point(aes(x = Spawners, y = log(Recruits), color = disturbedarea_prct_cs), alpha = 0.5, size = 2) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_low_cpd)), color = '#35978f', size = 1, alpha = 0.5) +
    geom_line(data = prediction_df, aes(x = spawners, y = log(recruits_predicted_high_cpd)), color = '#bf812d', size = 1, alpha = 0.5) +
    # geom_line(data = prediction_df, aes(x = spawners, y = log_RS), color = "black", size = 1, alpha = 0.5) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_low_cpd_lower), ymax = log(recruits_predicted_low_cpd_upper)), fill = "#35978f", alpha = 0.1) +
    geom_ribbon(data = prediction_df, aes(x = spawners, ymin = log(recruits_predicted_high_cpd_lower), ymax = log(recruits_predicted_high_cpd_upper)), fill = "#bf812d", alpha = 0.1) +
    labs(#title = "Ricker model with CPD, NPGO, ERSST", 
      x = "Spawners", y = TeX(r"($\log \left(Recruits\right)$)")) +
    scale_color_gradient2(name = 'CDA (%)',
                          low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 20)+
    theme_classic() +
    theme(legend.position = c(0.8,0.9),
          legend.background = element_rect(fill = alpha('white', 0.5)),
          legend.text = element_text(size = 7),
          legend.title = element_text(size = 8),
          axis.title.x = element_text(size = 8),
          axis.title.y = element_text(size = 8),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          plot.title = element_blank(),
          legend.key.width = unit(0.5, "cm"),
          legend.key.height = unit(1, "lines"),
          legend.spacing.y = unit(0.001, "cm")
    )
  
  
  
  
  
  
  return((p1))
}




plot_predicted_recruits <- function(posterior1 = ric_chm_cpd_ocean_covariates_logR,
                                    posterior2 = ric_chm_eca_ocean_covariates_logR,
                                    river = "CARNATION CREEK",  
                                    effect1 = "cpd",
                                    effect2 = "eca",
                                    species = "chum", 
                                    model1 = "CPD",
                                    model2 = "ECA"){
  if(species == "chum"){
    df <- ch20rsc 
    river_data <- ch20rsc %>% filter(River == river)
    river <- river_data$River_n[1]
    # df$sst.std <- (ch20rsc$spring_ersst-mean(ch20rsc$spring_ersst))/sd(ch20rsc$spring_ersst)
    
  } else if(species == "pink"){
    df <- pk10r
    river_data <- pk10r %>% filter(River == river)
    river <- river_data$River_n2[1]
    # df$sst.std <- (pk10r$spring_ersst-mean(pk10r$spring_ersst))/sd(pk10r$spring_ersst)
  }
  
  posterior_df_b_for <- posterior1 %>%
    select(starts_with(paste0('b_for_rv[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_for_rv',
                 values_to = "forestry") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  posterior_df_alpha <- posterior1 %>%
    select(starts_with(paste0('alpha_j[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'alpha_j',
                 values_to = "alpha_j") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  posterior_df_Smax <- posterior1 %>%
    select(starts_with(paste0('Smax[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'Smax',
                 values_to = "Smax") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  posterior_df_npgo <- posterior1 %>%
    select(starts_with(paste0('b_npgo_rv[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_npgo_rv',
                 values_to = "npgo") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  posterior_df_sst <- posterior1 %>%
    select(starts_with(paste0('b_sst_rv[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_sst_rv',
                 values_to = "sst") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  posterior_df2_b_for <- posterior2 %>% 
    select(starts_with(paste0('b_for_rv[',as.character(river),']'))) %>%
    pivot_longer(cols = everything(), 
                 names_to = 'River', 
                 names_prefix = 'b_for_rv',
                 values_to = "forestry") %>%
    mutate(River_n = as.numeric(str_extract(River, '\\d+'))) %>% 
    select(-River) %>% 
    mutate(River = river)
  
  #make a time series of median log Recruits with credible intervals using the spawner time series and forestry time series for each year
  
  predicted_recruits <- data.frame(BroodYear = river_data$BroodYear,
                                   Spawners = river_data$Spawners,
                                   Recruits = river_data$Recruits,
                                   predicted_log_recruits = apply(matrix(log(river_data$Spawners),ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j) ) + 
                                (matrix(posterior_df_alpha$alpha_j, ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j)) - as.matrix(1/posterior_df_Smax[,1])%*%river_data$Spawners + as.matrix(posterior_df_b_for[,1])%*%river_data$sqrt.CPD.std +
                                                          as.matrix(posterior_df_npgo[,1])%*%river_data$npgo.std + 
                                                          as.matrix(posterior_df_sst[,1])%*%river_data$sst.std ), 2, median),
                                predicted_log_recruits_upper <- apply(matrix(log(river_data$Spawners),ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j) ) + 
                                (matrix(posterior_df_alpha$alpha_j, ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j)) - as.matrix(1/posterior_df_Smax[,1])%*%river_data$Spawners + as.matrix(posterior_df_b_for[,1])%*%river_data$sqrt.CPD.std +
                                                          as.matrix(posterior_df_npgo[,1])%*%river_data$npgo.std + 
                                                          as.matrix(posterior_df_sst[,1])%*%river_data$sst.std ), 2, quantile, 0.975),
                                
                                predicted_log_recruits_lower <- apply(matrix(log(river_data$Spawners),ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j) ) + 
                                (matrix(posterior_df_alpha$alpha_j, ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j)) - as.matrix(1/posterior_df_Smax[,1])%*%river_data$Spawners + as.matrix(posterior_df_b_for[,1])%*%river_data$sqrt.CPD.std +
                                                          as.matrix(posterior_df_npgo[,1])%*%river_data$npgo.std + 
                                                          as.matrix(posterior_df_sst[,1])%*%river_data$sst.std ), 2, quantile, 0.025),
                                
                                forestry = river_data$sqrt.CPD.std,
                                
                                lowest_forestry = min(river_data$sqrt.CPD.std),
                                
                                predicted_log_recruits_low_forestry = apply(matrix(log(river_data$Spawners),ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j) ) + 
                                (matrix(posterior_df_alpha$alpha_j, ncol = length(river_data$Spawners), nrow = length(posterior_df_alpha$alpha_j)) - as.matrix(1/posterior_df_Smax[,1])%*%river_data$Spawners + as.matrix(posterior_df_b_for[,1])%*%rep(min(river_data$sqrt.CPD.std),length(river_data$sqrt.CPD.std)) +
                                                          as.matrix(posterior_df_npgo[,1])%*%river_data$npgo.std + 
                                                          as.matrix(posterior_df_sst[,1])%*%river_data$sst.std ), 2, median)
                                
                                
                                
                                   )
                                
                                
                                    
                                  
                                    
  
  #quick plot of log_recruits time series - observed and predicted
  plot1 <- ggplot() +
    geom_line(data = predicted_recruits, aes(x = BroodYear, y = predicted_log_recruits, color = "Predicted"), size = 1, alpha = 0.5) +
    geom_line(data = predicted_recruits, aes(x = BroodYear, y = predicted_log_recruits_low_forestry, color = "Predicted low forestry"), size = 1, alpha = 0.5) +
    geom_point(data = predicted_recruits, aes(x = BroodYear, y = log(Recruits),  fill = forestry), size = 2,shape = 21, color = "white",  alpha = 0.5) +
    # geom_line(data = predicted_recruits, aes(x = BroodYear, y = log(Recruits), color = "Observed"), size = 2, alpha = 0.5) +
    geom_ribbon(data = predicted_recruits, aes(x = BroodYear, ymin = predicted_log_recruits_lower, ymax = predicted_log_recruits_upper),
    fill = 'gray70', alpha = 0.4) +
    labs(x = "Brood Year", y = "log(Recruits)") +
    scale_color_manual(name = "Legend",
                       values = c("Predicted" = 'gray20',
                                  "Predicted low forestry" = '#A2C5AC')) +
    scale_fill_gradient2(name = 'CPD (standardized)',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0)+
    theme_classic() +
    theme(legend.position = "right",
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          plot.title = element_text(size = 14, hjust = 0.5))
  
  return(plot1)
  
  
}

```






# River-level data and model results


```{r echo=FALSE, fig.height=5, fig.width=6, results="asis"}



for(river in md_watersheds_total$River){
  
  cat('\n')
  cat("## ", river, "\n")
  cat('\n')
  
  #create flags for chum, pink even, and pink odd
  
  flag_chum = !is.na(md_watersheds_total$CU_chum[md_watersheds_total$River == river])
  flag_pink_even = !is.na(md_watersheds_total$CU_pink_Even[md_watersheds_total$River == river])
  flag_pink_odd = !is.na(md_watersheds_total$CU_pink_Odd[md_watersheds_total$River == river])
  
  
  if(flag_chum){
    river_data <- ch20rsc %>% filter(River == river)
  
  
  #time series of Spawners, Recruits, ECA, CPD
  # spawner_plot <- ggplot(river_data,aes(x = BroodYear, y = log(Spawners))) + 
  #   geom_line(size = 0.8, alpha = 0.7, color = "gray20") +
  #   geom_point(size = 2, alpha = 0.7, color = "gray20") +
  #   labs(y = "log(Spawners)", x = "Brood Year") +
  #   theme_classic() +
  #   theme(axis.title.x = element_text(size = 12),
  #         axis.title.y = element_text(size = 12),
  #         axis.text.x = element_text(size = 10),
  #         axis.text.y = element_text(size = 10))
  
  log_recruit_plot <- ggplot(river_data,aes(x = BroodYear, y = log(Recruits))) + 
    geom_line(size = 0.8, alpha = 0.7, color = "gray20") +
    geom_point(size = 2, alpha = 0.7, color = "gray20") +
    labs(y = "log (Recruits)", x = "Brood Year") +
    theme_classic() +
    theme(axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8))
  
  recruit_plot <- ggplot(river_data,aes(x = BroodYear, y = Recruits)) + 
    geom_line(size = 0.8, alpha = 0.7, color = "gray20") +
    geom_point(size = 2, alpha = 0.7, color = "gray20") +
    labs(y = "Recruits", x = "Brood Year") +
    theme_classic() +
    theme(axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8))
  
  ln_RS_plot <- ggplot(river_data,aes(x = BroodYear, y = ln_RS)) + 
    geom_line(size = 0.8, alpha = 0.7, color = "gray20") +
    geom_point(size = 2, alpha = 0.7, color = "gray20") +
    labs(y ="log (Recruits/Spawners)", x = "Brood Year") +
    theme_classic() +
    theme(axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8))
  
  eca_plot <- ggplot(river_data,aes(x = BroodYear, y = ECA_age_proxy_forested_only)) + 
    geom_line(size = 0.8, alpha = 0.7, color = '#7F6A93') +
    geom_point(size = 2, alpha = 0.7, color = '#7F6A93') +
    labs(y = "Equivalent\n Clearcut Area (ECA)", x = "Brood Year") +
    theme_classic() +
    theme(axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8))
  cpd_plot <- ggplot(river_data,aes(x = BroodYear, y = disturbedarea_prct_cs)) + 
    geom_line(size = 0.8, alpha = 0.7, color = '#A2C5AC') +
    geom_point(size = 2, alpha = 0.7, color = '#A2C5AC') +
    labs(y = "Cumulative\n Disturbed Area (%)", x = "Brood Year") +
    theme_classic() +
    theme(axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8))
  
  # print(recruit_plot / ln_RS_plot)
  # 
  # print(eca_plot / cpd_plot)
  effects_plot <- plot_all_effects_river_together(
    posterior1 = ric_chm_cpd_ocean_covariates_logR,
    river_name = str_to_title(river),
    river = unique(river_data$River_n)
  )
  
  change_plot <- plot_recruitment_change_river_together(
    posterior1 = ric_chm_cpd_ocean_covariates_logR,
    posterior2 = ric_chm_eca_ocean_covariates_logR,
    river_name = river,
    effect1 = "cpd",
    effect2 = "eca",
    species = "chum",
    model1 = "CPD",
    model2 = "ECA",
    hd = FALSE
  )
  
  spawner_recruit_plot <- plot_recruit_spawner_river_new(species = "chum",
                                 river_name = river,
                                 posterior = ric_chm_cpd_ocean_covariates_logR)
  
  
  print((eca_plot / cpd_plot / recruit_plot) + plot_layout(axis_titles = "collect") +
          
           plot_annotation(tag_levels = 'A',
                           title = paste("Data for Chum Salmon"))&
           theme(plot.tag.position = c(0.0, 1.0),
                 plot.title = element_text(size = 8),
                 plot.tag = element_text(size = 10, hjust = 0, vjust = 0, face = "bold")))
  
  cat('\n')
  cat('\n')
  
  print(((effects_plot+spawner_recruit_plot + plot_layout(widths = c(1,1)))/change_plot) +
           plot_annotation(tag_levels = 'A',title = paste("Model Results for Chum Salmon"))&
           theme(plot.tag.position = c(0.0, 1.0),
                 plot.title = element_text(size = 8),
                 plot.tag = element_text(size = 10, hjust = 0, vjust = 0, face = "bold")))
  
  
 
  
  cat('\n')
  }
  
  if(flag_pink_even | flag_pink_odd){
    river_data <- pk10r %>% filter(River == river)
    
    
    
    recruit_plot <- ggplot(river_data,aes(x = BroodYear, y = Recruits, group = Broodline, color = Broodline)) + 
    geom_line(size = 0.8, alpha = 0.7) +
    geom_point(size = 2, alpha = 0.7) +
    labs(y = "Recruits", x = "Brood Year") +
    scale_color_manual(values = c("Even" = "#89C9C4", "Odd" = "#C989A3")) +
    theme_classic() +
    theme(axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          axis.text.x = element_text(size = 8),
          axis.text.y = element_text(size = 8),
          legend.position = c(0.9,0.9)
          )
    
    effects_plot <- plot_all_effects_river_together(
      posterior1 = ric_pk_cpd_ersst_long_chain,
      river_name = str_to_title(river),
      river = unique(river_data$River_n)
    )
    
    change_plot <- plot_recruitment_change_river_together(
    posterior1 = ric_pk_cpd_ersst_long_chain,
    posterior2 = ric_pk_eca_ersst_long_chain,
    river_name = river,
    effect1 = "cpd",
    effect2 = "eca",
    species = "pink",
    model1 = "CPD",
    model2 = "ECA",
    hd = FALSE
  )
    
    
    if(flag_pink_even){
      spawner_recruit_plot_even <- plot_recruit_spawner_river_pink(species = "pink",
                                                         river_name = paste0(river,"_Even"),
                                                         posterior = ric_pk_cpd_ersst_long_chain)
    } else {
      spawner_recruit_plot_even <- ggplot() + theme_void() 
    }
    
    if(flag_pink_odd){
      spawner_recruit_plot_odd <- plot_recruit_spawner_river_pink(species = "pink",
                                                         river_name = paste0(river,"_Odd"),
                                                         posterior = ric_pk_cpd_ersst_long_chain)
    } else {
      spawner_recruit_plot_odd <- ggplot() + theme_void()
    }
    
    
      eca_plot <- ggplot(river_data,aes(x = BroodYear, y = ECA_age_proxy_forested_only)) + 
        geom_line(size = 0.8, alpha = 0.7, color = '#7F6A93') +
        geom_point(size = 2, alpha = 0.7, color = '#7F6A93') +
        labs(y = "Equivalent\n Clearcut Area (ECA)", x = "Brood Year") +
        theme_classic() +
        theme(axis.title.x = element_text(size = 10),
              axis.title.y = element_text(size = 10),
              axis.text.x = element_text(size = 8),
              axis.text.y = element_text(size = 8))
      cpd_plot <- ggplot(river_data,aes(x = BroodYear, y = disturbedarea_prct_cs)) + 
        geom_line(size = 0.8, alpha = 0.7, color = '#A2C5AC') +
        geom_point(size = 2, alpha = 0.7, color = '#A2C5AC') +
        labs(y = "Cumulative\n Disturbed Area (%)", x = "Brood Year") +
        theme_classic() +
        theme(axis.title.x = element_text(size = 10),
              axis.title.y = element_text(size = 10),
              axis.text.x = element_text(size = 8),
              axis.text.y = element_text(size = 8))
      
      print((eca_plot / cpd_plot / recruit_plot) + plot_layout(axis_titles = "collect") +
              
              plot_annotation(tag_levels = 'A',
                              title = paste("Data for Pink Salmon"))&
              theme(plot.tag.position = c(0.0, 1.0),
                    plot.title = element_text(size = 8),
                    plot.tag = element_text(size = 10, hjust = 0, vjust = 0, face = "bold")))
    
    
  
  cat('\n')
  cat('\n')
  
  if(flag_pink_odd){
   print(((effects_plot+spawner_recruit_plot_even/spawner_recruit_plot_odd + 
                    plot_layout(widths = c(1,1.2)))/change_plot) + plot_layout(heights = c(1.5,1)) +
           plot_annotation(tag_levels = 'A',title = paste("Model Results for Pink Salmon"))&
           theme(plot.tag.position = c(0.0, 1.0),
                 plot.title = element_text(size = 8),
                 plot.tag = element_text(size = 10, hjust = 0, vjust = 0, face = "bold")
                 )) 
  } else{
    print(((effects_plot+spawner_recruit_plot_even + 
                    plot_layout(widths = c(1,1.2)))/change_plot) + plot_layout(heights = c(1.5,1)) +
           plot_annotation(tag_levels = 'A',title = paste("Model Results for Pink Salmon"))&
           theme(plot.tag.position = c(0.0, 1.0),
                 plot.title = element_text(size = 8),
                 plot.tag = element_text(size = 10, hjust = 0, vjust = 0, face = "bold")
                 ))
  }
  
  cat('\n')
  
    
  }
  
  
}




```
