---
title: "Coastwide analysis of forestry impacts on BC Pacific Salmon"
author: "Maria Kuruvilla"
date: "Feb 2025"
output:
  powerpoint_presentation: default
  word_document:
    toc: true
  pdf_document:
    toc: true
  html_document:
    collapsed: false
    fig_caption: true
    highlight: espresso
    number_sections: true
    smooth_scroll: true
    theme: sandstone
    toc: true
    toc_float: true
---


```{=html}
<style type="text/css">

body{ /* Normal  */
      font-size: 13px;
  }
td {  /* Table  */
  font-size: 13px;
}
h1.title {
  font-size: 24px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 19px;
  color: Black;
}
h2 { /* Header 2 */
    font-size: 15px;
  color: Black;
}
h3 { /* Header 3 */
    font-size: 15px;
  color: Black;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache=FALSE)
options(max.print=23)
library(cmdstanr)
library(here);library(dplyr); library(stringr)
library(ggplot2)
library(tidyverse)
library(bayesplot)
library(patchwork)
library(hues)
library(GGally)
library(latex2exp)
```


## Model

### Beverton-Holt (BH):

- $log(R_{t,r}/S_{t,r}) = \alpha_t + \alpha_r - log(1+\frac{(e^{\alpha_t+\alpha_r}}{R_{k,r}}*S_{t,r}) + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$

## Model

### Beverton-Holt (BH):

- $log(R_{t,r}/S_{t,r}) = \alpha_t + \alpha_r - log(1+\frac{(e^{\alpha_t+\alpha_r}}{R_{k,r}}*S_{t,r}) + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$


- $log(R_{t,r}/S_{t,r}) = \alpha_r - log(1+(\frac{e^{\alpha_t+\alpha_r}}{R_{k,r}})*S_{t,r}) + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$


## Model

### Beverton-Holt (BH):

- $log(R_{t,r}/S_{t,r}) = \alpha_t + \alpha_r - log(1+\frac{(e^{\alpha_t+\alpha_r}}{R_{k,r}}*S_{t,r}) + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$


- $log(R_{t,r}/S_{t,r}) = \alpha_r - log(1+(\frac{e^{\alpha_t+\alpha_r}}{R_{k,r}})*S_{t,r}) + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$

- $log(R_{t,r}/S_{t,r}) = \alpha_r - log(1+\frac{e^{\alpha_t+\alpha_r}}{R_{k,r}}*S_{t,r}) + \beta_{for,r}*X_{t,r} + \beta_{npgo,r}*Y{t} + \beta_{sst,r}*Z{t,r} + \epsilon_{t,r}$

## Model

### Ricker:

- $log(R_{t,r}/S_{t,r}) = \alpha_t + \alpha_r - \frac{S_{t,r}}{Smax_r} + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$

## Model

### Ricker:

- $log(R_{t,r}/S_{t,r}) = \alpha_t + \alpha_r - \frac{S_{t,r}}{Smax_r} + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$

- $log(R_{t,r}/S_{t,r}) = \alpha_r - \frac{S_{t,r}}{Smax_r} + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$

## Model

### Ricker:

- $log(R_{t,r}/S_{t,r}) = \alpha_t + \alpha_r - \frac{S_{t,r}}{Smax_r} + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$

- $log(R_{t,r}/S_{t,r}) = \alpha_r - \frac{S_{t,r}}{Smax_r} + \beta_{for,r}*X_{t,r} + \epsilon_{t,r}$

- $log(R_{t,r}/S_{t,r}) = \alpha_r - \frac{S_{t,r}}{Smax_r} + \beta_{for,r}*X_{t,r} + \beta_{npgo,r}*Y{t} + \beta_{sst,r}*Z{t,r} + \epsilon_{t,r}$


```{r read_data}

# read in chum data

ch20rsc <- read.csv(here("origional-ecofish-data-models","Data","Processed","chum_SR_20_hat_yr_w_ersst.csv"))

# plot the number of recruits vs number of spawners

ch20rsc %>%
  ggplot(aes(x=Spawners, y=Recruits, color = "chum")) +
  geom_point(alpha = 0.1) +
  # scale_x_continuous(breaks = c(10,  1000, 100000)) +
  # log scale both axes
  scale_color_manual(values = c("chum" = "#69C5C5",
                              "pink-even" = "#C76F6F",
                              "pink-odd" = "#9E70A1")) +
  scale_x_log10(breaks = c(10,  1000, 100000), labels = scales::comma) +
  scale_y_log10(labels = scales::comma) +
  # scale_x_continuous(breaks = c(10,  1000, 100000)) +
  # geom_smooth(method = "lm") +
  labs(title = "Chum Salmon",
       x = "Number of Spawners",
       y = "Number of Recruits")+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        plot.title = element_text(size = 18, hjust = 0.5))

#save

ggsave(here("figures","chum_recruits_vs_spawners.png"), width = 8, height = 6, dpi = 300)

```




```{r read_pink_data}

# read in pink data

pk10r_e <- read.csv(here("origional-ecofish-data-models","Data","Processed","pke_SR_10_hat_yr_w_ersst.csv"))

#odd year pinks
pk10r_o <- read.csv(here("origional-ecofish-data-models","Data","Processed","pko_SR_10_hat_yr_w_ersst.csv"))


# Pink salmon - even/odd broodlines #####
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=='950-169400-00000-00000-0000-0000-000-000-000-000-000-000','SALMON RIVER 2',pk10r_o$River)
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=='915-765500-18600-00000-0000-0000-000-000-000-000-000-000','HEAD CREEK 2',pk10r_o$River)
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=='915-488000-41400-00000-0000-0000-000-000-000-000-000-000','WINDY BAY CREEK 2',pk10r_o$River)
pk10r_o$River=ifelse(pk10r_o$WATERSHED_CDE=="915-486500-05300-00000-0000-0000-000-000-000-000-000-000",'LAGOON CREEK 2',pk10r_o$River)
pk10r_o=pk10r_o[order(factor(pk10r_o$River),pk10r_o$BroodYear),]
rownames(pk10r_o)=seq(1:nrow(pk10r_o))

pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=='950-169400-00000-00000-0000-0000-000-000-000-000-000-000','SALMON RIVER 2',pk10r_e$River)
pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=='915-765500-18600-00000-0000-0000-000-000-000-000-000-000','HEAD CREEK 2',pk10r_e$River)
pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=='915-488000-41400-00000-0000-0000-000-000-000-000-000-000','WINDY BAY CREEK 2',pk10r_e$River)
pk10r_e$River=ifelse(pk10r_e$WATERSHED_CDE=="915-486500-05300-00000-0000-0000-000-000-000-000-000-000",'LAGOON CREEK 2',pk10r_e$River)
pk10r_e=pk10r_e[order(factor(pk10r_e$River),pk10r_e$BroodYear),]
rownames(pk10r_e)=seq(1:nrow(pk10r_e))


#normalize ECA 2 - square root transformation (ie. sqrt(x))
pk10r_o$sqrt.ECA=sqrt(pk10r_o$ECA_age_proxy_forested_only)
pk10r_o$sqrt.ECA.std=(pk10r_o$sqrt.ECA-mean(pk10r_o$sqrt.ECA))/sd(pk10r_o$sqrt.ECA)

#normalize CPD 2 - square root transformation (ie. sqrt(x))
pk10r_o$sqrt.CPD=sqrt(pk10r_o$disturbedarea_prct_cs)
pk10r_o$sqrt.CPD.std=(pk10r_o$sqrt.CPD-mean(pk10r_o$sqrt.CPD))/sd(pk10r_o$sqrt.CPD)

#normalize ECA 2 - square root transformation (ie. sqrt(x))
pk10r_e$sqrt.ECA=sqrt(pk10r_e$ECA_age_proxy_forested_only)
pk10r_e$sqrt.ECA.std=(pk10r_e$sqrt.ECA-mean(pk10r_e$sqrt.ECA))/sd(pk10r_e$sqrt.ECA)

#normalize CPD 2 - square root transformation (ie. sqrt(x))
pk10r_e$sqrt.CPD=sqrt(pk10r_e$disturbedarea_prct_cs)
pk10r_e$sqrt.CPD.std=(pk10r_e$sqrt.CPD-mean(pk10r_e$sqrt.CPD))/sd(pk10r_e$sqrt.CPD)


#standardize npgo
pk10r_o$npgo.std=(pk10r_o$npgo-mean(pk10r_o$npgo))/sd(pk10r_o$npgo)
pk10r_e$npgo.std=(pk10r_e$npgo-mean(pk10r_e$npgo))/sd(pk10r_e$npgo)

# pk10r_o$sst.std = (pk10r_o$spring_lighthouse_temperature-mean(pk10r_o$spring_lighthouse_temperature))/sd(pk10r_o$spring_lighthouse_temperature)
# pk10r_e$sst.std = (pk10r_e$spring_lighthouse_temperature-mean(pk10r_e$spring_lighthouse_temperature))/sd(pk10r_e$spring_lighthouse_temperature)

pk10r_o$sst.std = (pk10r_o$spring_ersst-mean(pk10r_o$spring_ersst))/sd(pk10r_o$spring_ersst)
pk10r_e$sst.std = (pk10r_e$spring_ersst-mean(pk10r_e$spring_ersst))/sd(pk10r_e$spring_ersst)


pk10r_o$escapement.t_1=pk10r_e$Spawners[match(paste(pk10r_o$WATERSHED_CDE,pk10r_o$BroodYear-1),paste(pk10r_e$WATERSHED_CDE,pk10r_e$BroodYear))]
pk10r_e$escapement.t_1=pk10r_o$Spawners[match(paste(pk10r_e$WATERSHED_CDE,pk10r_e$BroodYear-1),paste(pk10r_o$WATERSHED_CDE,pk10r_o$BroodYear))]

pk10r_o$Broodline='Odd'
pk10r_e$Broodline='Even'

L_o=pk10r_o%>%group_by(River)%>%summarize(l=n(),by=min(BroodYear),tmin=(min(BroodYear)-min(pk10r_o$BroodYear))/2+1,tmax=(max(BroodYear)-min(pk10r_o$BroodYear))/2)
L_e=pk10r_e%>%group_by(River)%>%summarize(l=n(),by=min(BroodYear),tmin=(min(BroodYear)-min(pk10r_e$BroodYear))/2+1,tmax=(max(BroodYear)-min(pk10r_e$BroodYear))/2)
L_o$River2=paste(L_o$River,'Odd',sep='_')
L_e$River2=paste(L_e$River,'Even',sep='_')
L_all=rbind(L_e,L_o)
L_all=L_all[order(factor(L_all$River2)),]

pk10r_o$ii=as.numeric(factor(pk10r_o$BroodYear))
pk10r_e$ii=as.numeric(factor(pk10r_e$BroodYear))

pk10r=rbind(pk10r_e,pk10r_o)
pk10r$River2=paste(pk10r$River,pk10r$Broodline,sep='_')
pk10r=pk10r[order(factor(pk10r$River2),pk10r$BroodYear),]


# plot the number of recruits vs number of spawners


ggplot() +
geom_point(data = pk10r %>% filter(Broodline == "Even"),
           aes(x=Spawners, y=Recruits, color = "pink-even"),alpha = 0.1) +
geom_point(data = pk10r %>% filter(Broodline == "Odd"),
           aes(x=Spawners, y=Recruits, color = "pink-odd"),alpha = 0.1) +
# scale_x_continuous(breaks = c(10,  1000, 100000)) +
# log scale both axes
scale_color_manual(values = c("chum" = "#69C5C5",
                              "pink-even" = "#C76F6F",
                              "pink-odd" = "#9E70A1")) +
scale_x_log10(breaks = c(10,  1000, 100000), labels = scales::comma) +
scale_y_log10(labels = scales::comma) +
# scale_x_continuous(breaks = c(10,  1000, 100000)) +
# geom_smooth(method = "lm") +
labs(title = "Pink Salmon",
     x = "Number of Spawners",
     y = "Number of Recruits")+
theme_classic()+
theme(legend.position = "none",
      axis.text.x = element_text(size = 12),
      axis.text.y = element_text(size = 12),
      axis.title.x = element_text(size = 16),
      axis.title.y = element_text(size = 16),
      plot.title = element_text(size = 18, hjust = 0.5))

#save
ggsave(here("figures","pink_recruits_vs_spawners.png"), width = 8, height = 6, dpi = 300)


```




```{r map}

ggplot() +
  geom_sf(data = bc_boundary, fill = "transparent", color = "slategray", alpha = 0.2) +
  # geom_point(data = lighthouse_locations, aes(x = long, y = lat), color = "darkred", size = 3, alpha=0.8) +
  geom_point(data=salmon_data_location, aes(x = X_LONG, y = Y_LAT, color = "chum"), size = 2, alpha=0.2) +
  geom_point(data=pke_salmon_data_location, aes(x = X_LONG, y = Y_LAT, color = "pink-even"), size = 2, alpha=0.2) +
  geom_point(data=pko_salmon_data_location, aes(x = X_LONG, y = Y_LAT, color = "pink-odd"), size = 2, alpha=0.2) +
  # geom_text(data = lighthouse_locations, aes(x = long, y = lat, label = location), 
  #           nudge_x = -1.5, nudge_y = 0.2, size = 3) +
  # ggrepel::geom_label_repel(data = lighthouse_locations, aes(x = long, y = lat, label = location),
  #                           nudge_x = -1.5, nudge_y = 0.2, size = 3, background = "white", alpha = 0.5) +
  scale_color_manual(values = c("chum" = "#69C5C5",
                                "pink-even" = "#C76F6F",
                                "pink-odd" = "#9E70A1")) +
  scale_x_continuous(limits = c(-133, -122)) +
  scale_y_continuous(limits = c(48, 56)) +
  guides(color = guide_legend(title = "Species"), override.aes = list(size = 4, alpha = 1))+
  xlab("Longitude") +
  ylab("Latitude") +
  theme_classic()+
  theme(legend.position = "right",
        legend.title = element_text(size = 14),
        legend.text = element_text(size = 12),
        axis.title = element_text(size = 16),
        axis.text = element_text(size = 12))


ggsave(here("figures","chum_pink_watersheds_location_map.png"), width = 8, height = 6, dpi = 300)




```


```{r models}

#plot theoretical Ricker curve

# Spawners

S <- seq(1, 50000, length.out = 1000)
a = 1.5
Smax <- 10000

R <- a*S*exp(-S/Smax)

# plot

ggplot() +
  geom_line(aes(x = S, y = R), color = "black") +
  labs(title = "Ricker",
       x = "Spawners",
       y = "Recruits")+
  scale_x_continuous(n.breaks = 3)+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(size = 24, hjust = 0.5))

#save

ggsave(here("figures","ricker_curve.png"), width = 8, height = 6, dpi = 300)

ggplot() +
  geom_line(aes(x = S, y = R/S), color = "black") +
  labs(title = "Ricker",
       x = "Spawners",
       y = latex2exp::TeX("$\\frac{Recrutits}{Spawners}$"))+
  scale_x_continuous(n.breaks = 3)+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(size = 24, hjust = 0.5))


#save

ggsave(here("figures","ricker_curve_ratio.png"), width = 8, height = 6, dpi = 300)



#log R/S

ggplot() +
  geom_line(aes(x = S, y = log(R/S)), color = "black") +
  labs(title = "Ricker",
       x = "Spawners",
       y = latex2exp::TeX("$\\log\\ (\\frac{Recrutits}{Spawners})$"))+
  scale_x_continuous(n.breaks = 3)+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(size = 24, hjust = 0.5))

#save

ggsave(here("figures","ricker_curve_log_ratio.png"), width = 8, height = 6, dpi = 300)



# theoretical BH curve

# Spawners

S <- seq(1, 50000, length.out = 1000)

a = 1.5

Rk <- 10000

R <- exp(a)*S/(1 + (exp(a)/Rk)*S)


# plot

ggplot() +
  geom_line(aes(x = S, y = R), color = "black") +
  labs(title = "Beverton-Holt",
       x = "Spawners",
       y = "Recruits")+
  scale_x_continuous(n.breaks = 3)+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(size = 24, hjust = 0.5))

#save

ggsave(here("figures","bh_curve.png"), width = 8, height = 6, dpi = 300)

ggplot() +
  geom_line(aes(x = S, y = R/S), color = "black") +
  labs(title = "Beverton-Holt",
       x = "Spawners",
       y = latex2exp::TeX("$\\frac{Recrutits}{Spawners}$"))+
  scale_x_continuous(n.breaks = 3)+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(size = 24, hjust = 0.5))

# save

ggsave(here("figures","bh_curve_ratio.png"), width = 8, height = 6, dpi = 300)

# log R/S

ggplot() +
  geom_line(aes(x = S, y = log(R/S)), color = "black") +
  labs(title = "Beverton-Holt",
       x = "Spawners",
       y = latex2exp::TeX("$\\log\\ (\\frac{Recrutits}{Spawners})$"))+
  scale_x_continuous(n.breaks = 3)+
  theme_classic()+
  theme(legend.position = "none",
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(size = 24, hjust = 0.5))

# save

ggsave(here("figures","bh_curve_log_ratio.png"), width = 8, height = 6, dpi = 300)


```



```{r model_fitting, fig.width=10, fig.height=8}

(plot_forestry_effect(posterior = bh_chm_cpd_st, effect = "CPD", species = "chum", model = "BH model with CPD", xlim = c(-1.2,1.2)) +
    plot_forestry_effect(posterior = bh_chm_eca_st, effect = "eca", species = "chum", model = "BH model with ECA", xlim = c(-1.2,1.2)))/(plot_forestry_effect(posterior = bh_chm_cpd, effect = "cpd", species = "chum", model = "BH model with CPD,\ncoastwide productivity", xlim = c(-1.2,1.2))+plot_forestry_effect(posterior = bh_chm_eca, effect = "eca", species = "chum", model = "BH model with ECA,\ncoastwide productivity", xlim = c(-1.2,1.2)))/(plot_forestry_effect(posterior = bh_chm_cpd_ersst, effect = "cpd", species = "chum", model = "BH model with CPD, NPGO, SST", xlim = c(-1.2,1.2))+plot_forestry_effect(posterior = bh_chm_eca_ersst, effect = "eca", species = "chum", model = "BH model with ECA, NPGO, SST", xlim = c(-1.2,1.2)))+plot_layout(guides = "collect")
# save

ggsave(here("figures","chum_forestry_effect_all_models_bh.png"), width = 10, height = 8, dpi = 300)



(plot_forestry_effect(posterior = bh_chm_cpd_ersst, effect = "cpd", species = "chum", model = "BH model with CPD, NPGO, SST", xlim = c(-1.2,1.2)) + plot_forestry_effect(posterior = bh_chm_eca_ersst, effect = "eca", species = "chum", model = "BH model with ECA, NPGO, SST", xlim = c(-1.2,1.2))) + plot_layout(guides = "collect")

# save

ggsave(here("figures","chum_forestry_effect_bh_npgo_ersst.png"), width = 10, height = 4, dpi = 300)


# pink

(plot_forestry_effect(posterior = bh_pk_cpd_ersst, effect = "cpd", species = "pink", model = "BH model with CPD, NPGO, SST", xlim = c(-0.5,0.5)) + plot_forestry_effect(posterior = bh_pk_eca_ersst, effect = "eca", species = "pink", model = "BH model with ECA, NPGO, SST", xlim = c(-0.5,0.5)))/(plot_sst_effect(posterior = bh_pk_cpd_ersst, effect = "cpd", species = "pink", model = "BH model with CPD, NPGO, SST", xlim = c(-0.5,0.5),color_by = "CU_name")  +plot_npgo_effect(posterior = bh_pk_cpd_ersst, effect = "cpd", species = "pink", model = "BH model with CPD, NPGO, SST", xlim = c(-0.5,0.5)))+ plot_layout(guides = "collect")

ggsave(here("figures","pink_forestry_npgo_sst_effect_bh_npgo_ersst.png"), width = 10, height = 8, dpi = 300)


# ricker models

(plot_forestry_effect(posterior = ric_chm_cpd_st, effect = "cpd", species = "chum", model = "Ricker model with CPD", xlim = c(-0.5,0.5)) + plot_forestry_effect(posterior = ric_chm_eca_st, effect = "eca", species = "chum", model = "Ricker model with ECA", xlim = c(-0.5,0.5)))/(plot_forestry_effect(posterior = ric_chm_cpd, effect = "cpd", species = "chum", model = "Ricker model with CPD,\ncoastwide productivity", xlim = c(-0.5,0.5)) + plot_forestry_effect(posterior = ric_chm_eca, effect = "eca", species = "chum", model = "Ricker model with ECA,\ncoastwide productivity", xlim = c(-0.5,0.5)))/(plot_forestry_effect(posterior = ric_chm_cpd_ersst, effect = "cpd", species = "chum", model = "Ricker model with CPD, NPGO, SST", xlim = c(-0.5,0.5)) + plot_forestry_effect(posterior = ric_chm_eca_ersst, effect = "eca", species = "chum", model = "Ricker model with ECA, NPGO, SST", xlim = c(-0.5,0.5)))  + plot_layout(guides = "collect")


#ggsave

ggsave(here("figures","chum_forestry_effect_all_models_ricker.png"), width = 10, height = 8, dpi = 300)


plot_forestry_effect(posterior = ric_chm_cpd_ersst, effect = "cpd", species = "chum", model = "Ricker model with CPD, NPGO, SST", xlim = c(-0.5,0.5)) + plot_forestry_effect(posterior = ric_chm_eca_ersst, effect = "eca", species = "chum", model = "Ricker model with ECA, NPGO, SST", xlim = c(-0.5,0.5)) + plot_layout(guides = "collect")

ggsave(here("figures","chum_forestry_effect_npgo_ersst_ricker.png"), width = 10, height = 4, dpi = 300)


# pink

(plot_forestry_effect(posterior = ric_pk_cpd_ersst, effect = "cpd", species = "pink", model = "Ricker model with CPD, NPGO, SST", xlim = c(-0.5,0.5)) + plot_forestry_effect(posterior = ric_pk_eca_ersst, effect = "eca", species = "pink", model = "Ricker model with ECA, NPGO, SST", xlim = c(-0.5,0.5)))/(plot_sst_effect(posterior = ric_pk_cpd_ersst, effect = "cpd", species = "pink", model = "Ricker model with CPD, NPGO, SST", xlim = c(-0.5,0.5),color_by = "CU_name")  +plot_npgo_effect(posterior = ric_pk_cpd_ersst, effect = "cpd", species = "pink", model = "Ricker model with CPD, NPGO, SST", xlim = c(-0.5,0.5)))+ plot_layout(guides = "collect")

ggsave(here("figures","pink_forestry_npgo_sst_effect_ricker_npgo_ersst.png"), width = 10, height = 8, dpi = 300)

```


```{r fig.width = 10, fig.height = 4}
(plot_sst_effect(posterior = ric_chm_cpd_ersst, effect = "cpd", species = "chum", model = "Ricker model with CPD, NPGO, SST", xlim = c(-0.25,0.25),color_by = "CU_name")  +plot_npgo_effect(posterior = ric_chm_cpd_ersst, effect = "cpd", species = "chum", model = "Ricker model with CPD, NPGO, SST", xlim = c(-0.25,0.25)))+ plot_layout(guides = "collect")

ggsave(here("figures","chum_sst_npgo_effect_ricker.png"), width = 10, height = 4, dpi = 300)

# bh

(plot_sst_effect(posterior = bh_chm_cpd_ersst, effect = "cpd", species = "chum", model = "BH model with CPD, NPGO, SST", xlim = c(-0.25,0.25),color_by = "CU_name")  +plot_npgo_effect(posterior = bh_chm_cpd_ersst, effect = "cpd", species = "chum", model = "BH model with CPD, NPGO, SST", xlim = c(-0.25,0.25)))+ plot_layout(guides = "collect")

ggsave(here("figures","chum_sst_npgo_effect_bh.png"), width = 10, height = 4, dpi = 300)

```



```{r producivity decline}

((plot_productivity_decline(posterior = bh_chm_cpd_ersst, effect = "cpd", species = "chum", model = "BH model with NPGO, SST", by_river = FALSE) + plot_productivity_decline(posterior = bh_chm_eca_ersst, effect = "eca", species = "chum", model = "BH model with NPGO, SST", by_river = FALSE)  )/(plot_productivity_decline(posterior = ric_chm_cpd_ersst, effect = "cpd", species = "chum", model = "Ricker model with NPGO, SST", by_river = FALSE) + plot_productivity_decline(posterior = ric_chm_eca_ersst, effect = "eca", species = "chum", model = "Ricker model with NPGO, SST", by_river = FALSE)    )) + plot_layout(guides = "collect") 


# save

ggsave(here("figures","chum_productivity_decline_all_models.png"), width = 10, height = 8, dpi = 300)

```


