---
title: "Theoretical Spawner Recruit Curves"
author: 'Maria Kuruvilla'
date: "April 2025"
output:
  html_document:
    collapsed: false
    fig_caption: true
    highlight: espresso
    number_sections: true
    smooth_scroll: true
    theme: sandstone
    toc: true
    toc_float: true
  pdf_document:
    toc: true
  word_document:
    toc: true
---

```{=html}
<style type="text/css">

body{ /* Normal  */
      font-size: 13px;
  }
td {  /* Table  */
  font-size: 13px;
}
h1.title {
  font-size: 24px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 19px;
  color: Black;
}
h2 { /* Header 2 */
    font-size: 15px;
  color: Black;
}
h3 { /* Header 3 */
    font-size: 15px;
  color: Black;
}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache=FALSE)
options(max.print=23)
library(cmdstanr)
library(here);library(dplyr); library(stringr)
library(ggplot2)
library(tidyverse)
library(bayesplot)
library(patchwork)
library(hues)
library(GGally)
library(latex2exp)
library(ggforce)
```


# Model

## Beverton-Holt (BH):

In this model, the effect of forestry is on the growth rate or the alpha term.

$log(R_{t,r}/S_{t,r}) = \alpha_r - log(1+(\frac{e^{\alpha_r + \beta_{forestry,r}*Forestry_{t,r} }}{R_{k,r}})*S_{t,r}) + \beta_{forestry,r}*Forestry_{t,r} + \rho \epsilon_{t-1,r}$

```{r bh}

bh_alpha <- function(St, alpha, beta, Rk, Forestry){
  log_Rt_St = alpha - log(1+(exp(alpha)/Rk)*St) + beta*Forestry
  return(exp(log_Rt_St)*St)
}

St <- seq(0,1000,10)

alpha <- 5.4
beta <- -0.5
Rk <- 500*(alpha)/(alpha-1)
Forestry <- c(-1,0,1)

df <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df[[paste0("Rt_",Forestry[i])]] <- bh_alpha(St, alpha, beta, Rk, Forestry[i])
}

df_long <- df %>% 
  pivot_longer(cols = -St, names_to = "Forestry", values_to = "Rt", names_prefix = "Rt_") %>% 
  mutate(Forestry = as.numeric(Forestry))


#plot Rt vs St

p1_bh_rk <- df_long %>% 
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1100)+
  #add 1 to 1 line
  # geom_abline(intercept = 0, slope = 1, linetype = "dashed")+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  annotate("text", x = 500, y = 200, label = TeX("$R = S e^{\\alpha - log(1+(\\frac{e^{\\alpha}}{R_{k}})*S) + \\beta_{forestry} Forestry}$"), parse = TRUE, size = 4)+
  theme_classic()

q1_bh_rk <- df_long %>% 
  as.data.frame() %>% 
  ggplot(aes(x=St, y=log(Rt/St), group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,6)+
  #add 1 to 1 line
  # geom_abline(intercept = 0, slope = 1, linetype = "dashed")+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "log (Recruits/Spawners)")+
  #annotate equation
  annotate("text", x = 500, y = -1, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha - log(1+(\\frac{e^{\\alpha}}{R_{k}})*S) + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3)+
  theme_classic()

bh_presentation_1 <- df_long %>% 
  # filter(Forestry == 0) %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1100)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  
  annotate("text", x = 500, y = 200, label = TeX("$R = \\frac{S e^{\\alpha + \\beta^{forestry} Forestry}}{1+(\\frac{e^{\\alpha}}{R_{k}})S}$"), parse = TRUE, size = 7)+
  geom_text(aes(label = "High Forestry", x = 250, y= 450), color = '#bf812d',
            size = 5) + 
  geom_text(aes(label = "Low Forestry", x = 250, y= 1070), color = '#35978f', size = 5) + 
  theme_classic()+
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 12))
bh_presentation_1


ggsave(here("figures", "presentation_bh_w_forestry_low_alpha.png"),
       plot = bh_presentation_1, 
       width = 8, height = 6, dpi = 300)

ggsave(here("figures", "june2025_presentation_bh_w_forestry.png"),
       plot = bh_presentation_1, 
       width = 8, height = 6, dpi = 300)

bh_presentation_linear <- df_long %>% 
  # filter(Forestry == 0) %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=log(Rt/St), group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,6)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "ln (Recruits/Spawners)")+
  annotate("text", x = 500, y = -1.5, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha - log(1+(\\frac{e^{\\alpha}}{R_{k}})S)+ \\beta^{forestry} Forestry $"), parse = TRUE, size = 7)+
  geom_text(aes(label = "High Forestry", x = 100, y= 0.5), color = '#bf812d',
            size = 5) + 
  geom_text(aes(label = "Low Forestry", x = 100, y= 5), color = '#35978f', size = 5) + 
  theme_classic()+
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 12))

bh_presentation_linear

ggsave(here("figures", "presentation_bh_linear_w_forestry_low_alpha.png"),
       plot = bh_presentation_linear, 
       width = 8, height = 6, dpi = 300)

ggsave(here("figures", "june_2025_presentation_bh_linear_w_forestry.png"),
       plot = bh_presentation_linear, 
       width = 8, height = 6, dpi = 300)


```


In this model the effect of forestry is on the growth rate or alpha term. This is a different formulation of the Beverton-Holt model with carrying capacity insteado maximum recruitment.

$log(R_{t,r}/S_{t,r}) = \alpha_r - log(1+(\frac{e^{\alpha_r + \beta_{forestry,r}*Forestry_{t,r} } - 1 }{R_{k,r}})*S_{t,r}) + \beta_{forestry,r}*Forestry_{t,r} + \rho \epsilon_{t-1,r}$

```{r bh_1}

bh_alpha_1 <- function(St, alpha, beta, K, Forestry){
  log_Rt_St = alpha - log(1+(exp(alpha+beta*Forestry) - 1)/K*St) + beta*Forestry
  return(exp(log_Rt_St)*St)
}

St <- seq(0,1000,10)

alpha <- 5.4
beta <- -0.5
K <- 500
Forestry <- c(-1,0,1)

df_1 <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df_1[[paste0("Rt_",Forestry[i])]] <- bh_alpha_1(St, alpha, beta, K, Forestry[i])
}

df_long_1 <- df_1 %>% 
  pivot_longer(cols = -St, names_to = "Forestry", values_to = "Rt", names_prefix = "Rt_") %>% 
  mutate(Forestry = as.numeric(Forestry))


#plot Rt vs St

p2_bh_alpha <-df_long_1 %>% 
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1100)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  annotate("text", x = 500, y = 200, label = TeX("$R = s e^{\\alpha - log(1+(\\frac{e^{\\alpha + \\beta_{forestry} Forestry } -1}{K})*S) + \\beta_{forestry} Forestry}$"), parse = TRUE, size = 4)+
  theme_classic()

q2_bh_alpha <- df_long_1 %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=log(Rt/St), group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,4)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "log (Recruits/Spawners)")+
  #annotate equation
  annotate("text", x = 500, y = -1, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha - log(1+(\\frac{e^{\\alpha + \\beta_{forestry} Forestry } -1}{K})*S) + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3)+
  theme_classic()

```

In this model, the effect of forestry is on the carrying capacity or K.

$log(R_{t,r}/S_{t,r}) = \alpha_r - log(1+\frac{(e^{\alpha_r} - 1)}{K_{t,r}}  S_{t,r}) + \rho\epsilon_{t-1,r}$


$log(K_{t,r}) = log(K_r) + \beta_{forestry,r}Forestry_{t,r}$

$K_{t,r} = K_r e^{\beta_{forestry,r}Forestry_{t,r}}$

```{r bh_2}

bh_alpha_2 <- function(St, alpha, beta, K, Forestry){
  K_for = K*exp(beta*Forestry)
  log_Rt_St = alpha - log(1+((exp(alpha) -1)/K_for)*St)
  return(exp(log_Rt_St)*St)
}

St <- seq(0,1000,10)

alpha <- 5.4
beta <- -0.5
K <- 500
Forestry <- c(-1,0,1)

df_2 <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df_2[[paste0("Rt_",Forestry[i])]] <- bh_alpha_2(St, alpha, beta, K, Forestry[i])
}

df_long_2 <- df_2 %>% 
  pivot_longer(cols = -St, names_to = "Forestry", values_to = "Rt", names_prefix = "Rt_") %>% 
  mutate(Forestry = as.numeric(Forestry))


p3_bh_K <- df_long_2 %>% 
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1100)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  annotate("text", x = 500, y = 200, label = TeX("$R = S e ^{\\alpha - log(1+\\frac{(e^{\\alpha} - 1)}{K e^{\\beta_{forestry} Forestry}} S) }$"), size = 4)+
  theme_classic()

q3_bh_K <- df_long_2 %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=log(Rt/St), group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,4)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Beverton-Holt Spawner Recruit Curve",
       x = "Spawners",
       y = "log (Recruits/Spawners)")+
  #annotate equation
  annotate("text", x = 500, y = -1, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha - log(1+\\frac{(e^{\\alpha} - 1)}{K e^{\\beta_{forestry} Forestry}} S) $"), size = 3)+
  theme_classic()



```




## Ricker:

In this model, the effect of forestry is on the density dependent term. This is the formulation of the Ricker model with the level of spawners at which recruitment is maximized.

$log(R_{t,r}/S_{t,r}) = \alpha_r - \frac{S_{t,r}}{Smax_r} + \beta_{forestry,r}*Forestry_{t,r} + \epsilon_{t-1,r}$



```{r ricker}

ricker_alpha <- function(St, alpha, beta, Smax, Forestry){
  log_Rt_St = alpha - St/Smax + beta*Forestry
  return(cbind(exp(log_Rt_St)*St, log_Rt_St))
}


St <- seq(0,1000,10)

alpha <- 1.2

beta <- -0.5

Smax <- 500

Forestry <- c(-1,0,1)

df_ricker <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df_ricker[[paste0("Rt_",Forestry[i])]] <- ricker_alpha(St, alpha, beta, Smax, Forestry[i])[,1]
  df_ricker[[paste0("ln_Rt_St_",Forestry[i])]] <- ricker_alpha(St, alpha, beta, Smax, Forestry[i])[,2]
}

df_long_ricker <- df_ricker %>% 
  pivot_longer(cols = starts_with("Rt_"), names_to = "Forestry", values_to = "Rt", names_prefix = "Rt_") %>% 
  mutate(Forestry = as.numeric(Forestry)) %>% 
  pivot_longer(cols = starts_with("ln_"), names_to = "Forestry2", values_to = "ln_Rt_St", names_prefix = "ln_Rt_St_") %>% 
  mutate(Forestry2 = as.numeric(Forestry2))

p4_ric_1 <- df_long_ricker %>% 
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1000)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  annotate("text", x =500, y = 200, label = TeX("$R = S e^{\\alpha - \\frac{S}{Smax} + \\beta_{forestry} Forestry$}"), parse = TRUE, size = 4)+
  
  theme_classic()


q4_ric_1 <- df_long_ricker %>%
  as.data.frame() %>% 
  select(ln_Rt_St, Forestry2, St) %>% 
  distinct() %>% 
  ggplot(aes(x=St, y=ln_Rt_St, group = Forestry2, color = Forestry2))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,2)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "log (Recruits/Spawners)")+
  #annotate equation
  annotate("text", x = 300, y = -1, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha - \\frac{S}{Smax} + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3)+
  theme_classic()

presentation_ric_1 <- df_long_ricker %>% 
  # filter(Forestry == 0) %>%
  as.data.frame() %>%
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1100)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  
  annotate("text", x =500, y = 200, label = TeX("$R = S e^{\\alpha - \\frac{S}{Smax} + \\beta^{forestry} Forestry$}"), parse = TRUE, size = 7)+
  geom_text(aes(label = "High Forestry", x = 500, y= 450), color = '#bf812d',
            size = 5) + 
  geom_text(aes(label = "Low Forestry", x = 500, y= 1050), color = '#35978f', size = 5) + 
  theme_classic()+
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 12))

presentation_ric_1

ggsave(here("figures", "presentation_ricker_w_forestry.png"), 
       plot = presentation_ric_1, 
       width = 8, height = 6, dpi = 300)

ggsave(here("figures", "presentation_june2025_ricker_w_forestry.png"), 
       plot = presentation_ric_1, 
       width = 8, height = 6, dpi = 300)

presentation_linear_ric_1 <- df_long_ricker %>% 
  # filter(Forestry2 == 0) %>%
  as.data.frame() %>%
  ggplot(aes(x=St, y=ln_Rt_St, group = Forestry2, color = Forestry2))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,2)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "ln (Recruits/Spawners)")+
  annotate("text", x = 350, y = -1, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha - \\frac{S}{Smax} + \\beta_{forestry} Forestry$"), parse = TRUE, size = 7)+
  geom_text(aes(label = "High Forestry", x = 100, y= 0), color = '#bf812d',
            size = 5) + 
  geom_text(aes(label = "Low Forestry", x = 100, y= 2), color = '#35978f', size = 5) + 
  theme_classic()+
  theme(legend.position = "none",
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 12))

ggsave(here("figures", "presentation_ricker_linear_w_forestry.png"),
       plot = presentation_linear_ric_1, 
       width = 8, height = 6, dpi = 300)

ggsave(here("figures", "june2025_presentation_ricker_linear_w_forestry.png"),
       plot = presentation_linear_ric_1, 
       width = 8, height = 6, dpi = 300)

```


In this model, the effect of forestry is on the growth rate or alpha. This is a different formulation of the Ricker model with carrying capacity instead of Smax.

$log(R_{t,r}/S_{t,r}) = \alpha_r - \frac{(\alpha_r + \beta_{forestry,r}*Forestry_{t,r} )S_{t,r}}{K} + \beta_{forestry,r}*Forestry_{t,r} + \epsilon_{t-1,r}$



```{r ricker_1}

ricker_alpha_1 <- function(St, alpha, beta, K, Forestry){
  log_Rt_St = alpha - (alpha + beta*Forestry)*St/K + beta*Forestry
  return(cbind(exp(log_Rt_St)*St, log_Rt_St))
}


St <- seq(0,1000,10)

alpha <- 1.2

beta <- -0.5

K = 500

Forestry <- c(-1,0,1)

df_ricker_1 <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df_ricker_1[[paste0("Rt_",Forestry[i])]] <- ricker_alpha_1(St, alpha, beta, K, Forestry[i])[,1]
  df_ricker_1[[paste0("ln_Rt_St_",Forestry[i])]] <- ricker_alpha_1(St, alpha, beta, K, Forestry[i])[,2]
}

df_long_ricker_1 <- df_ricker_1 %>% 
  pivot_longer(cols = starts_with("Rt"), names_to = "Forestry", values_to = "Rt", names_prefix = "Rt_") %>% 
  mutate(Forestry = as.numeric(Forestry))%>% 
  pivot_longer(cols =  starts_with("ln_Rt_St"), names_to = "Forestry2", values_to = "ln_Rt_St", names_prefix = "ln_Rt_St_") %>% 
  mutate(Forestry2 = as.numeric(Forestry2))

p5_ric_alpha <- df_long_ricker_1 %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1000)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  annotate("text", x = 500, y = 200, label = TeX("$R = S e ^{\\alpha - \\frac{(\\alpha + \\beta_{forestry} Forestry)S}{K} + \\beta_{forestry} Forestry$}"), parse = TRUE, size = 4)+
  theme_classic()

q5_ric_alpha  <- df_long_ricker_1 %>%
  as.data.frame() %>% 
  select(ln_Rt_St, Forestry2, St) %>% 
  distinct() %>% 
  ggplot(aes(x=St, y=ln_Rt_St, group = Forestry2, color = Forestry2))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,2)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "log (Recruits/Spawners)")+
  #annotate equation
  annotate("text", x = 500, y = -1, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha - \\frac{(\\alpha + \\beta_{forestry} Forestry)S}{K} + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3)+
  theme_classic()


```

In this model, the effect of forestry is on the carrying capacity or K. This is a different formulation of the Ricker model with K instead of Smax.

$log(R_{t,r}/S_{t,r}) = \alpha_r - \frac{(\alpha_r )S_{t,r}}{Ke^{\beta_{forestry,r}*Forestry_{t,r}}} + \epsilon_{t-1,r}$




```{r ricker_2}

ricker_alpha_2 <- function(St, alpha, beta, Smax, Forestry){
  K_forestry = K*exp(beta*Forestry)
  log_Rt_St = alpha - (alpha)*St/K_forestry
  return(cbind(exp(log_Rt_St)*St, log_Rt_St))
}


St <- seq(0,1000,10)

alpha <- 1.2

beta <- -0.5

K = 500

Forestry <- c(-1,0,1)

df_ricker_2 <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df_ricker_2[[paste0("Rt_",Forestry[i])]] <- ricker_alpha_2(St, alpha, beta, K, Forestry[i])[,1]
  df_ricker_2[[paste0("ln_Rt_St_",Forestry[i])]] <- ricker_alpha_2(St, alpha, beta, K, Forestry[i])[,2]
}

df_long_ricker_2 <- df_ricker_2 %>% 
  pivot_longer(cols = starts_with("Rt_"), names_to = "Forestry", values_to = "Rt", names_prefix = "Rt_") %>% 
  mutate(Forestry = as.numeric(Forestry)) %>% 
  pivot_longer(cols =  starts_with("ln_Rt_St"), names_to = "Forestry2", values_to = "ln_Rt_St", names_prefix = "ln_Rt_St_") %>% 
  mutate(Forestry2 = as.numeric(Forestry2))

p6_ric_K <- df_long_ricker_2 %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, group = Forestry, color = Forestry))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(0, 1000)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  annotate("text", x = 500, y = 200, label = TeX("$R = S e^{\\alpha - \\frac{\\alpha S}{Ke^{\\beta_{forestry} Forestry}} }$"), parse = TRUE, size = 4)+
  theme_classic()

q6_ric_K  <- df_long_ricker_2 %>%
  as.data.frame() %>% 
  select(ln_Rt_St, Forestry2, St) %>% 
  distinct() %>% 
  ggplot(aes(x=St, y=ln_Rt_St, group = Forestry2, color = Forestry2))+
  geom_line(size = 2, alpha = 0.5)+
  ylim(-2,2)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) + 
  labs(#title = "Ricker Spawner Recruit Curve",
       x = "Spawners",
       y = "log (Recruits/Spawners)")+
  #annotate equation
  annotate("text", x = 300, y = -1, label = TeX("$\\ln{\\frac{R}{S}} = \\alpha (1 - \\frac{S}{Ke^{\\beta_{forestry} Forestry}}) $"), parse = TRUE, size = 3)+
  theme_classic()




```

In this model, the forestry effect is on the density dependent term. This is a different formulation of the Ricker model with K instead of Smax.

$log(R_{t,r}/S_{t,r}) = \alpha_r - \frac{(\\alpha_r + \\beta_{forestry,r}*Forestry_{t,r} )S_{t,r}}{Ke^{\\beta_{forestry,r}*Forestry_{t,r}}} + \epsilon_{t-1,r}$



```{r plots, fig.width = 12, fig.height = 6}

# put all the bh figures together

bh_models <- ((p1_bh_rk + labs(title = "Density Independent") + 
  p2_bh_alpha + labs(title = "Productivity") + 
  p3_bh_K+ labs(title = "Carrying Capacity") ) + plot_layout(axes = "collect"))/((q1_bh_rk + q2_bh_alpha + q3_bh_K) + plot_layout(axes = "collect")) +
  plot_layout(guides = "collect") 

#log transform the y axis


ggsave(here("figures", "presentation_all_bh_models.png"), 
       plot = bh_models, 
       width = 12, height = 6, dpi = 300)


```



```{r plots2, fig.width = 11, fig.height = 6}

# put all the bh figures together


ricker_models <- (((p4_ric_1 + ylim(0,1100) + labs(title = "Density Independent") + 
  p5_ric_alpha + ylim(0,1100)+ labs(title = "Productivity") +
  p6_ric_K+ ylim(0,1100)+ labs(title = "Carrying Capacity"))+plot_layout(axes = "collect"))/((q4_ric_1 + 
  q5_ric_alpha + 
  q6_ric_K)+plot_layout(axes = "collect"))) +plot_layout(guides = "collect")
  
ggsave(here("figures", "presentation_all_ricker_models.png"), 
       plot = ricker_models, 
       width = 12, height = 6, dpi = 300)


```




## Ricker and Beverton-Holt model with the same $$\alpha$$


```{r ricker_bh}


St <- seq(0,1000,10)

alpha <- 1

beta <- -0.5

K = 500

Forestry <- c(-1,0,1)

df_ricker_bh <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df_ricker_bh[[paste0("Rt_ric_",Forestry[i])]] <- ricker_alpha_1(St, alpha, beta, K, Forestry[i])
  df_ricker_bh[[paste0("Rt_bh_",Forestry[i])]] <- bh_alpha_1(St, alpha*2, beta, K, Forestry[i])
}

df_long_ricker_bh <- df_ricker_bh %>% 
  pivot_longer(cols = -St, names_to = c("Model", "Forestry"), values_to = "Rt", names_sep = "_", names_prefix = "Rt_") %>%
  mutate(Forestry = as.numeric(Forestry))


df_long_ricker_bh %>%
  # filter(Forestry == 0) %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, linetype = Model, color = Forestry, group = interaction(Model, Forestry)))+
  geom_line(size = 1.5, alpha = 0.5)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) +
  scale_linetype_manual(name = 'Model', values = c("solid", "dashed"), labels = c("Beverton-Holt", "Ricker"))+
  labs(title = "Ricker and Beverton-Holt Spawner Recruit Curve with the same K",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  annotate("text", x = 500, y = 90, label = TeX("$R_{ricker} = \\alpha - \\frac{(\\alpha + \\beta_{forestry} Forestry)S}{K} + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3.5)+
  annotate("text", x = 500, y = 200, label = TeX("$R_{bh} = \\alpha - log(1+(\\frac{e^{\\alpha + \\beta_{forestry} Forestry } -1}{K})*S) + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3.5)+
  theme_classic()









```


## Ricker and Beverton-Holt model with the same $$\alpha$$

```{r ricker_bh_1}

St <- seq(0,1000,10)

alpha <- 2

beta <- -0.5

K = 500

Forestry <- c(-1,0,1)

df_ricker_bh_1 <- data.frame(St = St)

for (i in 1:length(Forestry)){
  df_ricker_bh_1[[paste0("Rt_ric_",Forestry[i])]] <- ricker_alpha_1(St, alpha, beta, K, Forestry[i])
  df_ricker_bh_1[[paste0("Rt_bh_",Forestry[i])]] <- bh_alpha_1(St, alpha, beta, K*2, Forestry[i])
}

df_long_ricker_bh_1 <- df_ricker_bh_1 %>% 
  pivot_longer(cols = -St, names_to = c("Model", "Forestry"), values_to = "Rt", names_sep = "_", names_prefix = "Rt_") %>%
  mutate(Forestry = as.numeric(Forestry))

df_long_ricker_bh_1 %>%
  
  # filter(Forestry == 0) %>%
  as.data.frame() %>% 
  ggplot(aes(x=St, y=Rt, linetype = Model, color = Forestry, group = interaction(Model, Forestry)))+
  geom_line(size = 1.5, alpha = 0.5)+
  scale_color_gradient2(name = 'Forestry',
                                        low = '#35978f', mid = 'gray', high = '#bf812d', midpoint = 0) +
  scale_linetype_manual(name = 'Model', values = c("solid", "dashed"), labels = c("Beverton-Holt", "Ricker"))+
  labs(title = "Ricker and Beverton-Holt Spawner Recruit Curve with the same alpha",
       x = "Spawners",
       y = "Recruits")+
  #annotate equation
  
  annotate("text", x = 500, y = 90, label = TeX("$R_{ricker} = \\alpha - \\frac{(\\alpha + \\beta_{forestry} Forestry)S}{K} + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3.5)+
  annotate("text", x = 500, y = 200, label = TeX("$R_{bh} = \\alpha - log(1+(\\frac{e^{\\alpha + \\beta_{forestry} Forestry } -1}{K})*S) + \\beta_{forestry} Forestry$"), parse = TRUE, size = 3.5)+
  theme_classic()



```




